---
title: "R Notebook"
output: html_notebook
---

```{r}
cwd<-getwd()

setwd("~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/")

source("DEV-OutcomesPreAndPost_R_2023-06-21_2348.r")

#setwd(cwd)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
#let's use good old data.table, I miss it
library(data.table)
library(dplyr)

dev2_pp_dt_all_sessions<- data.table(data)

#dev2_ru_session01 <- dev2_ru_dt_all_sessions[redcap_event_name %in% c("session_0_arm_1","t1_arm_1","session_1_arm_1")]

table(dev2_pp_dt_all_sessions$redcap_event_name)

```

Let's get some participant information....

```{r}
ppt_id <- c("dev_id","date_0"#,"address"
            ,"birthsex","dob","race___1","race___2","race___3","race___4","race___5","race___6","race___7","race___8")
#only store info relevant to participant ID
participant_list_raw <- dev2_pp_dt_all_sessions[,ppt_id,with=FALSE]
#now remove missing data columns
blank_by_row <- rowSums(is.na(participant_list_raw))+rowSums(participant_list_raw=="",na.rm = TRUE)
#remove rows with the least amount of information
# ppt_list_clean.1 <- participant_list_raw[blank_by_row<max(blank_by_row)]
# ppt_list_clean <- ppt_list_clean.1[stringr::str_detect(ppt_list_clean.1$dev_id,"DEV\\d\\d\\d") & ppt_list_clean.1$dob!="",]

```

Let's strip out irrelevant rows.

```{r}
blank_by_row <- rowSums(is.na(dev2_pp_dt_all_sessions))+rowSums(dev2_pp_dt_all_sessions=="",na.rm = TRUE)

#remove rows with no content other than a DEV ID.
dev2_pp_dt_all_sessions.1 <- dev2_pp_dt_all_sessions[blank_by_row<max(blank_by_row)]

```

Then combine to get rows representing subjects rather than events. Columns are already unique, we just need to make it so.

First let's test that:
 - Group by dev_id
 - within each group, count the number of rows

```{r}
vars_per_subj_by_columns <- dev2_pp_dt_all_sessions.1 %>% group_by(dev_id) %>% summarise_each(
  funs=list(function(x){sum(!is.na(x))}))

max_var_count <- apply(vars_per_subj_by_columns,2,max)
max_var_count[max_var_count>1]
cols_with_one_entry_per_subject <- names(max_var_count)[max_var_count==1]
```


```{r}
dev2_pp_dt_all_sessions.1 %>% select(dev_id, bmi_category,redcap_event_name.factor,bmi_category.factor)
```

So we need to separate out the columns that are already recorded across sessions....alternatively we can COMBINE the multiple columns that store multiple values.

Do that with columns that:
 - end in a numeric value
 - have max one entry per subject.
 
```{r}
cols_ending_in_numeric <- colnames(dev2_pp_dt_all_sessions.1)[stringr::str_which(colnames(dev2_pp_dt_all_sessions.1),"^((?!race).)*_\\d$") %>% .[!is.na(.)]]

cols_to_coalesce <- intersect(cols_with_one_entry_per_subject,cols_ending_in_numeric)
```


```{r}
#only store info relevant to participant ID
ppt_anon_list_raw <- dev2_pp_dt_all_sessions.1[,ppt_id,with=FALSE]
#now remove missing data columns
blank_by_row <- rowSums(is.na(ppt_anon_list_raw))+rowSums(ppt_anon_list_raw=="",na.rm = TRUE)
#remove rows with the least amount of information
ppt_list_clean.1 <- ppt_anon_list_raw[blank_by_row<max(blank_by_row)]
ppt_list_clean <- ppt_list_clean.1[stringr::str_detect(ppt_list_clean.1$dev_id,"DEV\\d\\d\\d") & ppt_list_clean.1$dob!="",]
```

Process some demographic data
```{r}

race_cols <- colnames(ppt_list_clean)[grepl("race__",colnames(ppt_list_clean))]
race_data <- ppt_list_clean[,..race_cols]
#get labels
race_data_labels <- unlist(lapply(stringr::str_match_all(label(race_data),pattern = "choice\\=(.*)\\)"),function(x)(x[,2])))

race_friendly_colnames<-paste0("Race ",race_data_labels)
setnames(race_data,race_cols,race_friendly_colnames)

ppt_list_clean<-cbind(ppt_list_clean,race_data)


```


Amend some Sex data that was missing in Redcap and only available via a slack message: https://uosanlab.slack.com/archives/C6733G9QB/p1690932451744859?thread_ts=1690931783.736439&cid=C6733G9QB

```{r}
table(ppt_list_clean$birthsex)
ppt_list_clean$birthsex[ppt_list_clean$dev_id=="DEV124"]<-1
ppt_list_clean$birthsex[ppt_list_clean$dev_id=="DEV154"]<-1
ppt_list_clean$birthsex[ppt_list_clean$dev_id=="DEV234"]<-2
```


```{r}
ppt_list_w_data <- ppt_list_clean
for (cname in cols_to_coalesce){
  
  non_null_rows <- !is.na(dev2_pp_dt_all_sessions.1[,cname,with=FALSE])[,1]
  
  ppt_list_w_data <- merge(ppt_list_w_data, dev2_pp_dt_all_sessions.1[non_null_rows,c("dev_id",cname),with=FALSE],by="dev_id",all.x=TRUE)
}


library(lubridate)
save(ppt_list_w_data,file = paste0("~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/ppt_list_w_data_",today(),".Rdata"))
```

 