---
title: "Power analysis"
output:
  html_document:
    df_print: paged
---


```{r}
#install.packages("tidystats")
library(stringr)
library(dplyr)
library(ggplot2)
library(rstatix)

load("~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/scored_data_w_demographics.RData")
scored<-scored_with_demographics
rm(scored_with_demographics)
scored$score <- as.numeric(scored$score)
scored$scale_name <- sub("-","_",scored$scale_name)
```

```{r}

#
scored %>% filter(scale_name %in% c("FCI")) %>% select(scored_scale) %>% unique

```
```{r}
scored$scale_name %>% unique
```


Now get BMI

```{r}
load("../../../files/data/ppt_list_w_data.RData")
#our primary health outcome measure
ppt_health_outcomes <- ppt_list_w_data %>% select(dev_id,bf_1) %>% filter(!is.na(bf_1))
rm(ppt_list_w_data)

```

## Health measures include:
 - Percent Body Fat (`bf_1`)
 - BMI (`bmi_0`)
 
## Behavioral outcome measures

We also have behavioral outcome measures:

 - Food Frequency Questionnaire. Very closely related to the Food Craving Inventory so that needs to be considered carefully.
 


## Self-report predictor variables to investigate 

Which predictor scales should we include?
 
Need the behavioral and self-report imho
 
Before we decide which to include, perhaps we put them into categories: obvious theoretical link to outcome (3), possible theoretical link to outcome (2), no clear theoretical link to outcome (1).
 
Listing them by these categories we get:

### Obvious theoretical link to outcome

These are explicitly designed to measure constructs we are concerned about, like self control or habits.

 - Brief Self Control Scale
 - Self-reported Habit Index
 - Tempest Self-Regulation Questionnaire for Eating
 - Treatment Self-Regulation Questionnaire
 - Barratt Impulsiveness Scale
 - Eating Dysregulation Measure
 - Food Craving Inventory
 - Restraint Scale


### Possible theoretical link to outcome

These aren't explicitly designed to measure constructs we are concerned about, but there are theoretical reasons or at least 'stories you could tell' to expect a link to outcome.

 - Big Five
 - Planfulness
 - Regulatory Mode Questionnaire
 - Responses to Failure Scale
 - Perceived Competence Scale
 
 

### No clear theoretical link to outcome

For this category it is unclear why we would expect any link to the outcome (eating). Some are included in DEV more because of their theoretical link to the treatment rather than to baseline level of obesity.

 - Need for Cognition Scale
 - Vividness of Visual Imagery Questionnaire
 - Intrinsic Motivation Inventory
 - Adverse Childhood Experiences

### In DEV but not a construct of interest

These are in DEV but aren't psychological constructs and so I'm not considering them.

  - International Physical Activity Questionnaire
  - Demographic measures
  
## Behavioral predictor variables

 - WTP
    - price given for healthy foods
    - price given for unhealthy foods
    - difference between the above two
 - ROC
    - [regulate - look] craving reduction for healthy foods
    - [regulate - look] craving reduction for unhealthy foods
    - balance of the above two
 - SST
    - Participant behavioral net response bias toward healthy foods
    - Participant behavioral net response bias toward unhealthy foods
    - difference between the above
  

# Checking for presence of each of these  

Do we have these scales? let's take a look.

```{r}
table(scored$scale_name)
```


Group 1:

 - Brief Self Control Scale - Y
 - Self-reported Habit Index - N- no rubric
 - Tempest Self-Regulation Questionnaire for Eating - N- no rubric
 - Treatment Self-Regulation Questionnaire - N- no rubric
 - Barratt Impulsiveness Scale - N- no rubric
 - Eating Dysregulation Measure - Y
 - Food Craving Inventory - Y
 - Restraint Scale - N- no rubric


## the following were NOT pre-registered.
Group 2:

These aren't explicitly designed to measure constructs we are concerned about, but there are theoretical reasons or at least 'stories you could tell' to expect a link to outcome.

 - Big Five - Y
 - Planfulness -Y
 - Regulatory Mode Questionnaire - N- no rubric
 - Responses to Failure Scale - N- no rubric
 - Perceived Competence Scale - N- no rubric


<!-- ## scramble -->

<!-- ```{r} -->
<!-- #get a scrambled dataset we can use to test the pipeline without revealing any results -->
<!-- scored_dummy <- scored -->
<!-- scored_dummy$score <-sample(scored_dummy$score,length(scored_dummy$score)) -->
<!-- scored <- scored_dummy -->

<!-- ppt_health_outcomes$bmi_0<-sample(ppt_health_outcomes$bmi_0,nrow(ppt_health_outcomes)) -->
<!-- ppt_health_outcomes$bf_1<-sample(ppt_health_outcomes$bf_1,nrow(ppt_health_outcomes)) -->
<!-- ``` -->





## analysis (left over from previous analysis)

Get the first survey for each scale:
```{r}
scored$survey_num <- as.numeric(str_trim(str_match(scored$survey_name,"[DEV Session \\s][\\d+][\\sSurveys]")))
first_survey_for_scale<-scored %>% group_by(scale_name) %>% dplyr::summarise("first_survey"=min(survey_num))

#then select it.
scored_fs <- scored %>%
  merge(first_survey_for_scale,by="scale_name") %>%
  filter(survey_num==first_survey)

print("survey used for each scale:")
print(first_survey_for_scale)

sapply(unique(scored_fs$scale_name),function(sn){list(sn=unique(scored_fs[scored_fs$scale_name==sn,"scored_scale"]))})
```


```{r}

#iterate through each of our scales, and test their correlation with FCI and FFQ

#scales where there's a promote-prevent
promote_minus_prevent <- scored_fs %>% 
  #filter for FFQ
  filter(scale_name %in% c("FFQ","FCI")) %>%
  #filter for the two cols we're interested in
  filter(scored_scale %in% c("cancer_promoting","cancer_preventing","craved_cancer_promoting","liked_cancer_promoting","craved_cancer_preventing","liked_cancer_preventing")) %>%
  #throw it out wide
  select(SID,scored_scale,score,survey_name,scale_name) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  #create a composite measure
  mutate("cancer_promoting_minus_preventing"=cancer_promoting-cancer_preventing,
         "cancer_promoting_minus_preventing_craved"=craved_cancer_promoting-craved_cancer_preventing,
         "cancer_promoting_minus_preventing_liked"=liked_cancer_promoting-liked_cancer_preventing
         ) %>%
  #wide across the surveys so that we can compare the surveys
  select(scale_name,survey_name,SID,cancer_promoting_minus_preventing,cancer_promoting_minus_preventing_craved,cancer_promoting_minus_preventing_liked) %>% 
  tidyr::pivot_wider(id_cols=c("SID","survey_name"),
                     names_from=scale_name,
                     values_from=c(
    "cancer_promoting_minus_preventing",
    "cancer_promoting_minus_preventing_craved",
    "cancer_promoting_minus_preventing_liked")
    )

single_scale_predictors_mean <- c("BSCS","EDM","cSES")

single_scale_values_mean <- scored_fs %>% 
    #filter for FFQ
  filter(scale_name %in% single_scale_predictors_mean) %>%
  #filter for the two cols we're interested in
  #filter(scored_scale %in% c("mean")) %>%#unnecessary
  #throw it out wide
  select(SID,scored_scale,score,survey_name,scale_name) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  #wide across the surveys so that we can compare the surveys
  select(scale_name,survey_name,SID,mean) %>% 
  tidyr::pivot_wider(id_cols=c("SID","survey_name"),
                     names_from=scale_name,
                     values_from=c("mean")
    )


single_scale_predictors_sum <- c("TESQ_E","TRSQ","BIS_11","RS")

single_scale_values_sum <- scored_fs %>% 
  #filter for FFQ
  filter(scale_name %in% single_scale_predictors_sum) %>%
  #throw it out wide
  select(SID,scored_scale,score,survey_name,scale_name) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  #wide across the surveys so that we can compare the surveys
  select(scale_name,survey_name,SID,sum) %>% 
  tidyr::pivot_wider(id_cols=c("SID","survey_name"),
                     names_from=scale_name,
                     values_from=c("sum")
    )
single_scale_values<- merge(single_scale_values_mean,single_scale_values_sum,by=c("SID","survey_name"),all=TRUE)

#now merge these

scales_wide<-merge(promote_minus_prevent,single_scale_values,by=c("SID","survey_name"),all=TRUE)

ppt_data_wide_raw_1 <- merge(scales_wide,ppt_health_outcomes,by.x="SID",by.y="dev_id",all=TRUE)

```

```{r}
scored_fs %>% filter(scale_name=="DEMO") %>% .$scored_scale %>% unique

scored_fs_demo_zscored <- scored_fs %>% filter(scale_name=="DEMO")
ses_grouped<-c("zipcode_median_income_acs", "household_income_per_person","household_income_level_medamount","education_own")

scored_fs_demo_zscored <- scored_fs_demo_zscored %>% data.frame %>% group_by(scored_scale) %>% 
  filter(scored_scale %in% ses_grouped) %>% 
  mutate(
  score_zscore=(score-mean(score,na.rm=TRUE))/sd(score,na.rm=TRUE),
  score_mean = mean(score,na.rm=TRUE),
  score_sd =sd(score,na.rm=TRUE)) %>% ungroup
#get a zscore of each

scored_fs_demo_zscored$score<- scored_fs_demo_zscored$score_zscore

scored_fs_demo_zscored_wide <- scored_fs_demo_zscored %>% 
  select(SID,survey_name,score,scored_scale) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  rowwise() %>%
  mutate(ses_aggregate=mean(c(education_own,zipcode_median_income_acs,household_income_per_person,household_income_level_medamount)))


```


```{r}
#Now do multi-scale predictors
#Big5, Planfulness
multi_scale_predictor_list <- list(BFI =c("agreeableness","conscientiousness","extraversion","neuroticism","openness"),
                           PLAN = c("cognitive_strategies","mental_forecasting","temporal_orientation"),
                           ACES = c("sum","abuse","divorced_separated","household_dysfunction","neglectful_parenting"),
                           RTFS = c("factor_1", "factor_2"),
                           SRHI = c("healthy","unhealthy","sum"),
                           DEMO = c("mcarthur_social_standing")
                           
                           )

#go through the table and label every subscale that we want to keep
scored_fs$INCLUDE_SUBSCALE <- FALSE
for (scale_x in names(multi_scale_predictor_list)){
  print(scale_x)
  for(subscale_x in multi_scale_predictor_list[[scale_x]]){
    print(subscale_x)
    scored_fs[scored_fs$scale_name==scale_x & scored_fs$scored_scale==subscale_x,"INCLUDE_SUBSCALE"] <- TRUE
  }
}

scored_multi <- scored_fs[scored_fs$INCLUDE_SUBSCALE,]

scored_multi$scale_subscale_name <- paste0(scored_multi$scale_name,"_",scored_multi$scored_scale)

multi_scale_values <- scored_multi %>% 
  #throw it out wide
  select(SID,survey_name,score,scale_subscale_name) %>% tidyr::pivot_wider(names_from = scale_subscale_name,values_from = score)

ppt_data_wide_raw_2 <- merge(ppt_data_wide_raw_1,multi_scale_values,by=c("SID","survey_name"),all=TRUE)


ppt_data_wide <- merge(ppt_data_wide_raw_2,scored_fs_demo_zscored_wide,by=c("SID","survey_name"),all=TRUE)
```


```{r}
#grabs the FIRST score for each item per participant.
col_list <- lapply(colnames(ppt_data_wide %>% select(-survey_name,-SID)), function(col){
  return(ppt_data_wide %>% select(-survey_name) %>% .[,c("SID",col)] %>% filter(!is.na(.[col])) %>% group_by(SID) %>% summarise("{col}":=first(.data[[col]])))
})
data_by_ppt <- purrr::reduce(col_list, left_join,by="SID")



```

Now we do some contrasts we haven't done yet...

```{r}
data_by_ppt$SRHI_healthy_minus_unhealthy <- data_by_ppt$SRHI_healthy-data_by_ppt$SRHI_unhealthy
```

Now we need to get the non-scale social values in here.

<!-- ```{r} -->
<!-- ppt_data_wide_dummy <- ppt_data_wide -->

<!-- for (cn in colnames(ppt_data_wide_dummy)[3:length(colnames(ppt_data_wide_dummy))]){ -->
<!--   print(cn) -->
<!--   ppt_data_wide_dummy[,cn]<-sample(ppt_data_wide_dummy[,cn],length(ppt_data_wide_dummy[,cn])) -->
<!-- } -->
<!-- rm(ppt_data_wide) -->
<!-- ``` -->

### Exploratory analysis for health special issue

Here we'll follow a few basic steps:

 - Loop through each source and do these analyses. This might occur several times because we'll need to arrange different sources in unique ways.
 - Add each test of interest to a grand table of findings, storing the label, effect, and the p-value
 - Do FWE test on the findings to determine the end result


For each set, we'll need to loop through the three outcome measures, and then loop through the relevant predictor variables. We do two-way correlations to understand which should be followed up.



label the variables
```{r}
IVs <- c("cancer_promoting_minus_preventing_craved_FCI","cancer_promoting_minus_preventing_liked_FCI",
         "EDM","BSCS","ACES_sum",
         "SRHI_sum","SRHI_healthy_minus_unhealthy","TESQ_E","TRSQ","RS","RTFS_factor_1","RTFS_factor_2","BIS_11",
         "ses_aggregate","DEMO_mcarthur_social_standing","cSES"
         
         #'BFI_agreeableness', 'BFI_conscientiousness', 'BFI_extraversion', 'BFI_neuroticism', 'BFI_openness', 
         #'PLAN_cognitive_strategies', 'PLAN_mental_forecasting', 'PLAN_temporal_orientation'
         )
DVs <- c("cancer_promoting_minus_preventing_FFQ","bf_1")
```


Can we merge across surveys to only include the first survey taken? For each of these scales, participants may have only done a selection of the surveys

This would look like:

 - For each participant and column, merge across surveys and only include the FIRST result in each survey.
 

```{r}


#now we estimate R^2....
correlation_df <- data.frame()
for (DV in DVs){
  for(IV in IVs){
    #for (dn in draw_names){
      #pairwise_not_na <- (is.na(data_by_ppt %>% filter(survey_name==dn) %>% .[,IV])==FALSE) &  (is.na(data_by_ppt %>% filter(survey_name==dn) %>% .[,DV])==FALSE)
    pairwise_not_na <- (is.na(data_by_ppt %>% .[,IV])==FALSE) &  (is.na(data_by_ppt %>% .[,DV])==FALSE)
    if(sum(pairwise_not_na)>0){
      print(paste0(DV,",", IV, " (",as.character(sum(pairwise_not_na)) , " values)"))
        cor_res <-cor.test(
          #data_by_ppt %>% filter(survey_name==dn) %>% .[,IV],
          #data_by_ppt %>% filter(survey_name==dn) %>% .[,DV],
          data_by_ppt[[IV]],
          data_by_ppt[[DV]],
          use = "complete.obs"
        )
        #print(paste0("r value of ", as.character(cor_res$estimate)))
        cat(".")
        cor_df <- data.frame(
          "v1"=DV,
          "v2"=IV,
          "n"=sum(pairwise_not_na),
#          "survey"=dn,
          "statistic" = cor_res$statistic,
          "df" = cor_res$parameter,
          "p.value" = cor_res$p.value,
          "estimate"=cor_res$estimate,
          "ci_lower" = cor_res$conf.int[[1]],
          "ci_upper" = cor_res$conf.int[[2]]
          
          
        )
        correlation_df <-rbind(correlation_df,cor_df)
          #correlation_list <- correlation_list %>% add_stats(cor_res)
          

     # }#else{
        #print(paste("no valid column pair for:",IV,",", DV, " (",dn,")"))
      #}
   }
  }
}

#correlation_df <-  tidy_stats_to_data_frame(correlation_list)



```
```{r}
data_by_ppt %>% group_by(DEMO_mcarthur_social_standing) %>% summarise(mean_ffq=mean(cancer_promoting_minus_preventing_FFQ,na.rm=TRUE))

cor.test(data_by_ppt$DEMO_mcarthur_social_standing,data_by_ppt$cancer_promoting_minus_preventing_liked_FCI)
cor.test(data_by_ppt$DEMO_mcarthur_social_standing,data_by_ppt$cancer_promoting_minus_preventing_craved_FCI)
cor.test(data_by_ppt$DEMO_mcarthur_social_standing,data_by_ppt$cancer_promoting_minus_preventing_FFQ)
```


```{r}
ggplot(data_by_ppt,aes(DEMO_mcarthur_social_standing,data_by_ppt$cancer_promoting_minus_preventing_FFQ))+geom_point()
```

## Result

```{r}
View(correlation_df)
```


Now, let's split these up into their families of predictions based on https://osf.io/gvus3:


```{r}
mcc <- function(cor_df){
  cor_df$p.value_adjusted <- p.adjust(cor_df$p.value,method="fdr")
  return(cor_df)
}
```

## Pre-registered predictions

### 1. Food valuation

### 2. Craving

```{r}
craving_ivs <- c("cancer_promoting_minus_preventing_craved_FCI")
craving_cors <- mcc(correlation_df[correlation_df$v2 %in% craving_ivs,])

craving_cors[c("v1","v2","n","p.value","p.value_adjusted")]
```

the Food Craving Inventory is rleated to the Food Frequency Questionnaire but not body fat percentage.

### 3. Habit

```{r}

habit_ivs <- c("SRHI_sum","SRHI_healthy_minus_unhealthy")
habit_cors <- mcc(correlation_df[correlation_df$v2 %in% habit_ivs,])

habit_cors[c("v1","v2","n","p.value","p.value_adjusted")]
```
The Self Report Habit Index is related to the Food Frequency Questionnaire but not body fat percentage.

overall habit score is not related to health outcomes.


### 4. Inhibitory control and self regulation

```{r}
inhibitory_ivs <- c("TESQ_E","TRSQ",
         "BIS_11","BSCS",
         "EDM","RS")
inhibitory_cors <- mcc(correlation_df[correlation_df$v2 %in% inhibitory_ivs,])

inhibitory_cors[c("v1","v2","n","p.value","p.value_adjusted")]
```

The Tempest Self-Regulation Questionnaire for Eating is related to the Food Frequency Questionnaire. 

No other inhibitory control measure relates to the Food Frequency Questionnaire before or after controlling for multiple comparisons. While we still need to add planned behavioral measures I do not expect this will affect the adjusted significance of any of the existing findings. The TESQ_E is strongly relqted to FFQ in a way that will survive a lot more multiple comparisons than this.

It would be useful to examine the breakdown of the TESQ_E subscales and their relationship to the food frequency questionnaire.

There are some items that were significant when not adjusted for the multiple comparison, but not significant after adjusting:

 - BIS_11 * FFQ
 - Body Fat % * RS
 
 
It might be worth using these findings to guide neural investigation even as we acknowledge the evidence is not strong for them as main effects.

### 5. Socioeconomic

```{r}
ses_ivs <- c("ACES_sum","ses_aggregate","DEMO_mcarthur_social_standing","cSES")
ses_cors <- mcc(correlation_df[correlation_df$v2 %in% ses_ivs,])

ses_cors[c("v1","v2","n","p.value","p.value_adjusted","estimate")]
```
There is one relationship that is significant before but not after adjusting for multiple comparisons FFQ * the mcarthur ladder appears significant (p=0.02); however the estimate is in the reverse direction of that anticipated. 


## Supplementary analysis

Of the above I have already examined one outcome, Responses to Failure Scale. This appears to be a fairly robust finding:


```{r}
rtfs_ivs <- c("RTFS_factor_1","RTFS_factor_2")
rtfs_cors <- mcc(correlation_df[correlation_df$v2 %in% rtfs_ivs,])

rtfs_cors[c("v1","v2","n","p.value","p.value_adjusted","estimate")]
```
It isn't clear that it fits into any of the above categories.

There are additional items we might examine:

 - Big Five
 - Planfulness
 - Regulatory Mode Questionnaire
 - Perceived Competence Scale
 - Mother and/or father education
 - All the individual levels of income that we only tested in aggregate for this analysis ((a) zipcode typical income, (b) total household income, (c) household per capita income, (d) education level)

Seems cheeky to go and do a _second_ pre-registration for these so I recommend just going ahead with a further analysis; however I want to seek input from others first.