---
title: "R Notebook"
output: html_notebook
---

Looking at basic exploratory analysis of the summary stats for response inhibition.



```{r}
#install.packages("tidystats")
library(stringr)
library(dplyr)
library(ggplot2)
library(rstatix)
data_path <- "../../../files/data/"

load("~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/scored_data_w_demographics.RData")
dropbox_file_dir = "~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"
scored<-scored_with_demographics
rm(scored_with_demographics)
scored$score <- as.numeric(scored$score)
scored$scale_name <- sub("-","_",scored$scale_name)
```

```{r}

#
scored %>% filter(scale_name %in% c("FCI")) %>% select(scored_scale) %>% unique

```
```{r}
scored$scale_name %>% unique
```


Now get BMI

```{r}
load("../../../files/data/ppt_list_w_data.RData")

ppt_list_w_data$date_0<-as.Date(ppt_list_w_data$date_0)
ppt_list_w_data$dob<-as.Date(ppt_list_w_data$dob)
ppt_list_w_data$age365<- as.numeric((ppt_list_w_data$date_0-ppt_list_w_data$dob)/365)

#our primary health outcome measure
ppt_health_outcomes <- ppt_list_w_data %>% select(dev_id,bf_1,weight_0,height_0,birthsex,age365,bmi_0,bmi_1) %>% filter(!is.na(bf_1))

ppt_health_outcomes$bmi <- ifelse(!is.na(ppt_health_outcomes$bmi_0),ppt_health_outcomes$bmi_0,ppt_health_outcomes$bmi_1)
rm(ppt_list_w_data)

#remove data of implausible bf_1 values
ppt_health_outcomes$bf_1[ppt_health_outcomes$bf_1<13]<-NA


#get a bf_1 score with sex regressed out
#do we want to regress out height as well???

#plot(ppt_health_outcomes$height_0,ppt_health_outcomes$bf_1)

#hmm that's fairly strong. 
#but does it hold after controlling for sex?
#I think it would be good to regress out height as well.
#so we will use a linear model to predict bf_1 from height and sex. 
cor.test(ppt_health_outcomes[birthsex==1, height_0],ppt_health_outcomes[birthsex==1,bf_1])
cor.test(ppt_health_outcomes[birthsex==2, height_0],ppt_health_outcomes[birthsex==2,bf_1])
#it does not.

#what about age?
cor.test(ppt_health_outcomes[birthsex==1, age365],ppt_health_outcomes[birthsex==1,bf_1])
cor.test(ppt_health_outcomes[birthsex==2, age365],ppt_health_outcomes[birthsex==2,bf_1])
#might be a moderate correlation within birth sex levels of age. so it is worth norming for age too
#if we were just controlling for a single variable we could z-score
#but now we're doing age as well.
#which would imply not z-scoring, we should use a linear model.

bf_model <- lm(bf_1~birthsex+age365, ppt_health_outcomes)
summary(bf_model)
#ppt_health_outcomes$bf_1_controlled <-NULL <- bf_model$residuals
ppt_health_outcomes$bf_1_controlled[as.numeric(rownames(bf_model$model))] <- bf_model$residuals

#simple model just zscoring within sex
#that allows for a more inuitive interpretation than errors from a linear model.
ppt_health_outcomes %<>% group_by(birthsex) %>% mutate(
  bf_1_bsexnormedzs = (bf_1-mean(bf_1,na.rm = TRUE))/sd(bf_1,na.rm = TRUE),
  
)


#cor.test(ppt_health_outcomes$birthsex,ppt_health_outcomes$bf_1)
plot(ppt_health_outcomes$birthsex,ppt_health_outcomes$bf_1)
#cor.test(ppt_health_outcomes$birthsex,ppt_health_outcomes$bf_1_bsexnormedzs)
#plot(ppt_health_outcomes$birthsex,ppt_health_outcomes$bf_1_bsexnormedzs)

#plot(ppt_health_outcomes$birthsex,ppt_health_outcomes$bf_1_controlled)

plot(ppt_health_outcomes$bf_1,ppt_health_outcomes$bf_1_controlled)




```


```{r}
min(ppt_health_outcomes$age365)

max(ppt_health_outcomes$age365)

table(ppt_health_outcomes$birthsex)
```



Now get behavioral measures.

```{r}

#sst_pes <- readr::read_csv("https://www.dropbox.com/s/vaubgp23y5j0m5g/post_error_slowing.csv?dl=0")
sst_pes <- readr::read_csv(paste0("~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/", "post_error_slowing.csv"))
sst_pes_simple <- readr::read_csv(paste0("~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/", "post_error_slowing_simple_approach.5.7.22.csv"))
#should be wave 1 by default.
sst_data_1 <- readr::read_csv(file=paste0(data_path,"sst_summary_stats_by_run.csv"))
sst_data_2 <- readr::read_csv(file=paste0(data_path,"sst_pre_analyzed_stats.csv"))
sst_data_1_w1 <- sst_data_1%>%filter(runid==1)%>% select(-runid)
sst_data_2_w1 <- sst_data_2 %>% filter(wave==1) %>% select(-wave)
sst_w1 <- merge(sst_data_1_w1,sst_data_2_w1,by.x ="subid",by.y="SubjectLabel",all = TRUE) %>%
  merge(sst_pes[,2:ncol(sst_pes)],by="subid",all=TRUE) %>%
  merge(sst_pes_simple[,2:ncol(sst_pes_simple)],by="subid",all=TRUE)



roc_data <- readr::read_csv(file=paste0(data_path,"roc_summary_stats.csv"))
load(file=paste0(data_path,"wtp_summary_stats_across_runs.Rdata"))




#need to group across run
roc_data_across_runs<- roc_data %>% select(-run) %>% group_by(subjectID,wave) %>% summarise(across(everything(), mean))
roc_data_across_runs_w1 <- roc_data_across_runs %>%filter(wave==1)%>% select(-wave)

wtp_across_runs_wide <- wtp_across_runs %>% select(subject, value_level_mean, health_cond,wave) %>% group_by(subject,wave) %>% spread("health_cond","value_level_mean") %>% ungroup
wtp_across_runs_wide$unhealthy_minus_healthy <- wtp_across_runs_wide$unhealthy - wtp_across_runs_wide$healthy
wtp_across_runs_wide_w1 <- wtp_across_runs_wide%>%filter(wave==1) %>% select(-wave)
colnames(wtp_across_runs_wide_w1) <- paste0("WTP_",colnames(wtp_across_runs_wide_w1))



#sst_data$wave <- 1
colnames(sst_w1) <- paste0("SST_",colnames(sst_w1))
roc_data_across_runs_w1 <- rename(roc_data_across_runs_w1,c(subid=subjectID))
colnames(roc_data_across_runs_w1) <- paste0("ROC_",colnames(roc_data_across_runs_w1))
#roc_data_across_runs$runid <- as.double(stringr::str_match(roc_data_across_runs$run,"run(\\d)")[,2])

behavioral_data <- merge(sst_w1,roc_data_across_runs_w1,by.x=c("SST_subid"),by.y="ROC_subid",all = TRUE)
behavioral_data <- rename(behavioral_data,c(subid=SST_subid))
behavioral_data <- merge(behavioral_data,wtp_across_runs_wide_w1,by.x = "subid",by.y="WTP_subject",all=TRUE)



```







## analysis (left over from previous analysis)

Get the first survey for each scale:
```{r}
scored$survey_num <- as.numeric(str_trim(str_match(scored$survey_name,"[DEV Session \\s][\\d+][\\sSurveys]")))
first_survey_for_scale<-scored %>% group_by(scale_name) %>% dplyr::summarise("first_survey"=min(survey_num))

#then select it.
scored_fs <- scored %>%
  merge(first_survey_for_scale,by="scale_name") %>%
  filter(survey_num==first_survey)

print("survey used for each scale:")
print(first_survey_for_scale)


```




```{r}
sapply(unique(scored_fs$scale_name),function(sn){list(sn=unique(scored_fs[scored_fs$scale_name==sn,"scored_scale"]))})
```


```{r}

#iterate through each of our scales, and test their correlation with FCI and FFQ

#scales where there's a promote-prevent
promote_minus_prevent <- scored_fs %>% 
  #filter for FFQ
  filter(scale_name %in% c("FFQ","FCI")) %>%
  #filter for the two cols we're interested in
  filter(scored_scale %in% c(
    "cancer_promoting","cancer_preventing","craved_cancer_promoting","liked_cancer_promoting","craved_cancer_preventing","liked_cancer_preventing")) %>%
  #throw it out wide
  select(SID,scored_scale,score,survey_name,scale_name) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  #create a composite measure
  mutate("cancer_promoting_minus_preventing"=cancer_promoting-cancer_preventing,
         "cancer_promoting_minus_preventing_craved"=craved_cancer_promoting-craved_cancer_preventing,
         "cancer_promoting_minus_preventing_liked"=liked_cancer_promoting-liked_cancer_preventing
         ) %>%
  #wide across the surveys so that we can compare the surveys
  select(scale_name,survey_name,SID,cancer_promoting_minus_preventing,
         cancer_promoting_minus_preventing_craved,cancer_promoting_minus_preventing_liked,
         cancer_promoting,cancer_preventing
         ) %>% 
  tidyr::pivot_wider(id_cols=c("SID","survey_name"),
                     names_from=scale_name,
                     values_from=c(
    "cancer_promoting_minus_preventing",
    "cancer_promoting_minus_preventing_craved",
    "cancer_promoting_minus_preventing_liked",
    "cancer_promoting","cancer_preventing"
    )
    )

single_scale_predictors_mean <- c("BSCS","EDM","cSES")

single_scale_values_mean <- scored_fs %>% 
    #filter for FFQ
  filter(scale_name %in% single_scale_predictors_mean) %>%
  #filter for the two cols we're interested in
  #filter(scored_scale %in% c("mean")) %>%#unnecessary
  #throw it out wide
  select(SID,scored_scale,score,survey_name,scale_name) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  #wide across the surveys so that we can compare the surveys
  select(scale_name,survey_name,SID,mean) %>% 
  tidyr::pivot_wider(id_cols=c("SID","survey_name"),
                     names_from=scale_name,
                     values_from=c("mean")
    )





single_scale_predictors_sum <- c("TRSQ","BIS_11","RS","PCS")

single_scale_values_sum <- scored_fs %>% 
  #filter for FFQ
  filter(scale_name %in% single_scale_predictors_sum) %>%
  #throw it out wide
  select(SID,scored_scale,score,survey_name,scale_name) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  #wide across the surveys so that we can compare the surveys
  select(scale_name,survey_name,SID,sum) %>% 
  tidyr::pivot_wider(id_cols=c("SID","survey_name"),
                     names_from=scale_name,
                     values_from=c("sum")
    )
single_scale_values<- merge(single_scale_values_mean,single_scale_values_sum,by=c("SID","survey_name"),all=TRUE)

#now merge these

scales_wide<-merge(promote_minus_prevent,single_scale_values,by=c("SID","survey_name"),all=TRUE)

ppt_data_wide_raw_1 <- merge(scales_wide,ppt_health_outcomes,by.x="SID",by.y="dev_id",all=TRUE)

```

```{r}
scored_fs %>% filter(scale_name=="DEMO") %>% .$scored_scale %>% unique

scored_fs_demo_zscored <- scored_fs %>% filter(scale_name=="DEMO")
ses_grouped<-c("zipcode_median_income_acs", "household_income_per_person","household_income_level_medamount","education_own")

scored_fs_demo_zscored <- scored_fs_demo_zscored %>% data.frame %>% group_by(scored_scale) %>% 
  filter(scored_scale %in% ses_grouped) %>% 
  mutate(
  score_zscore=(score-mean(score,na.rm=TRUE))/sd(score,na.rm=TRUE),
  score_mean = mean(score,na.rm=TRUE),
  score_sd =sd(score,na.rm=TRUE)) %>% ungroup
#get a zscore of each

scored_fs_demo_zscored$score<- scored_fs_demo_zscored$score_zscore

scored_fs_demo_zscored_wide <- scored_fs_demo_zscored %>% 
  select(SID,survey_name,score,scored_scale) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  rowwise() %>%
  mutate(ses_aggregate=mean(c(education_own,zipcode_median_income_acs,household_income_per_person,household_income_level_medamount)))


```



```{r}
#Now do multi-scale predictors
#Big5, Planfulness
multi_scale_predictor_list <- list(BFI =c("agreeableness","conscientiousness","extraversion","neuroticism","openness"),
                           PLAN = c("cognitive_strategies","mental_forecasting","temporal_orientation"),
                           ACES = c("sum","abuse","divorced_separated","household_dysfunction","neglectful_parenting"),
                           RTFS = c("factor_1", "factor_2"),
                           SRHI = c("healthy","unhealthy","sum"),
                           DEMO = c("mcarthur_social_standing"),
                           IPAQ = c("sittinghours", "moderateminutes", "vigorousminutes", "walkingminutes"),
                           RMQ = c("assessment", "lie",        "locomotion"),
                           IMI = c("value_usefulness", "perceived_choice", "perceived_competence", "effort_importance", "interest_enjoyment"),
                           NCS = c("get_job_done","intellectual_task", "abstract_thinking", "like_responsibility", "thinking_not_exciting",
                                   "think_minimally", "thinking_not_fun", "avoid_depth", "deliberating_issues", "prefer_little_thought",
                                   "relief_not_satisfaction", "satisfaction_in_deliberating", "thought_appealing", "total", "tasks_little_thought",
                                   "solve_puzzles", "small_daily_projects", "new_solutions_to_problems", "prefer_complex"
                                   ),
                           TESQ_E = unique(scored_fs[scored_fs$scale_name=="TESQ_E","scored_scale"])
                           )

#go through the table and label every subscale that we want to keep
scored_fs$INCLUDE_SUBSCALE <- FALSE
for (scale_x in names(multi_scale_predictor_list)){
  print(scale_x)
  for(subscale_x in multi_scale_predictor_list[[scale_x]]){
    cat(subscale_x)
    scored_fs[scored_fs$scale_name==scale_x & scored_fs$scored_scale==subscale_x,"INCLUDE_SUBSCALE"] <- TRUE
  }
}

scored_multi <- scored_fs[scored_fs$INCLUDE_SUBSCALE,]

scored_multi$scale_subscale_name <- paste0(scored_multi$scale_name,"_",scored_multi$scored_scale)

multi_scale_values <- scored_multi %>% 
  #throw it out wide
  select(SID,survey_name,score,scale_subscale_name) %>% tidyr::pivot_wider(names_from = scale_subscale_name,values_from = score)

ppt_data_wide_raw_2 <- merge(ppt_data_wide_raw_1,multi_scale_values,by=c("SID","survey_name"),all=TRUE)


ppt_data_wide <- merge(ppt_data_wide_raw_2,scored_fs_demo_zscored_wide,by=c("SID","survey_name"),all=TRUE)
```


```{r}
#grabs the FIRST score for each item per participant.
col_list <- lapply(colnames(ppt_data_wide %>% select(-survey_name,-SID)), function(col){
  return(ppt_data_wide %>% select(-survey_name) %>% .[,c("SID",col)] %>% filter(!is.na(.[col])) %>% group_by(SID) %>% summarise("{col}":=first(.data[[col]])))
})
data_by_ppt <- purrr::reduce(col_list, left_join,by="SID")



```


##Now get the behavioral data


```{r}
data_by_ppt <- merge(data_by_ppt,behavioral_data,by.x="SID",by.y="subid",all.x = TRUE,all.y=FALSE)

```

Now we do some contrasts we haven't done yet...

```{r}
data_by_ppt$SRHI_healthy_minus_unhealthy <- data_by_ppt$SRHI_healthy-data_by_ppt$SRHI_unhealthy
data_by_ppt$RTFS_f1_minus_f2 <- data_by_ppt$RTFS_factor_1-data_by_ppt$RTFS_factor_2
#Craig CL,Marshall A , Sjostrom M et al. International Physical Activity Questionnaire: 12 country reliability and validity Med Sci Sports Exerc 2003;August
#also available on the IPAQ scoring protocol in the DEV Dropbox, page 5
#Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/Measures/Measures_Questionnaires/IPAQ Scoring Protocol.pdf
data_by_ppt$IPAQ_walkingMETminutes <- data_by_ppt$IPAQ_walkingminutes* 3.3
data_by_ppt$IPAQ_moderateMETminutes <- data_by_ppt$IPAQ_moderateminutes* 4.0
data_by_ppt$IPAQ_vigorousMETminutes <- data_by_ppt$IPAQ_vigorousminutes* 8.0
data_by_ppt$IPAQ_total_METminutes <-data_by_ppt$IPAQ_walkingMETminutes + data_by_ppt$IPAQ_moderateMETminutes+ data_by_ppt$IPAQ_vigorousMETminutes
weight_in_kg <- data_by_ppt$weight_0* 0.453592 #convert from pounds to kg
data_by_ppt$IPAQ_MET_kCal <- data_by_ppt$IPAQ_total_METminutes * weight_in_kg/60


# data_by_ppt$birthsex_factor<-""
# data_by_ppt$birthsex_factor[data_by_ppt$birthsex==1]<-"Female"
# data_by_ppt$birthsex_factor[data_by_ppt$birthsex==2]<-"Male"
# data_by_ppt$birthsex_factor<-factor(data_by_ppt$birthsex_factor,levels=c("Female","Male"))

data_by_ppt <- data_by_ppt %>% mutate(
  birthsex_factor =
    factor(case_when(
      birthsex==1 ~ "Female",
      birthsex==2 ~ "Male"
    ),levels=c("Female","Male"))
)
                                            
```



### get the modified FFQ

This is done here, rather than earlier, because it needs gender.


```{r}

#we need two things here:
#(1)  list of FFQ by individual item"
      #Can't use "scored"
      #need to use survey_long_clean from scorequaltrics_workflow. It's saved here:

load(paste0(dropbox_file_dir,"/raw_survey_data.RData"))
#(2)  list of birthsex. this is done easily enough with:
birthsex_key <- data_by_ppt[c("SID","birthsex_factor")]

#1=female, 2=male



source("ffq_revision/get_ffq_v2.R")

ffq_v2_values <- score_ffqv2(surveys_long_clean,birthsex_key)
colnames(ffq_v2_values) <- paste0("FFQ_v2_",colnames(ffq_v2_values))


```

```{r}
data_by_ppt <- merge(data_by_ppt,ffq_v2_values,by.x="SID",by.y="FFQ_v2_SID",all.x = TRUE,all.y=FALSE)

```


Now we need to get the non-scale social values in here.

<!-- ```{r} -->
<!-- ppt_data_wide_dummy <- ppt_data_wide -->

<!-- for (cn in colnames(ppt_data_wide_dummy)[3:length(colnames(ppt_data_wide_dummy))]){ -->
<!--   print(cn) -->
<!--   ppt_data_wide_dummy[,cn]<-sample(ppt_data_wide_dummy[,cn],length(ppt_data_wide_dummy[,cn])) -->
<!-- } -->
<!-- rm(ppt_data_wide) -->
<!-- ``` -->


### wide-stage data cleaning

#### outlier removal

https://www.active.com/fitness/calculators/bodyfat

Classification	Women (% Fat)	Men (% Fat)
Essential Fat	10-12%	2-4%
Athletes	14-20%	6-13%
Fitness	21-24%	14-17%
Acceptable	25-31%	18-25%
Obese	32% +	25% +



With ~200 subjects, how often would we expect subjects 2 or 3 or 4 SD outside the mean?

```{r}

for (coln in colnames(data_by_ppt)[2:ncol(data_by_ppt)]){
  class(data_by_ppt[[coln]])
  if(sum(is.na(data_by_ppt[[coln]]))<length(data_by_ppt[[coln]])){
    
    na_row <- is.na(unlist(data_by_ppt[coln]))
    col_vals <- unlist(data_by_ppt[!na_row,coln])
    if(class(col_vals)!="factor"){
      col_sids <- data_by_ppt[!na_row,"SID"]
      col_mean<-mean(col_vals)
      col_sd<-sd(col_vals)
      outliers_4sigma <- (col_vals < col_mean - col_sd * 4) | (col_vals > col_mean + col_sd * 4)
      outliers_5sigma <- (col_vals < col_mean - col_sd * 5) | (col_vals > col_mean + col_sd * 5)
      if(sum(outliers_4sigma)+sum(outliers_5sigma)>0){
        print(paste(coln, ": 4 sigma outliers are:",paste(data_by_ppt[outliers_4sigma,"SID"],collapse = ","), "; 5 sigma outliers are:",paste(data_by_ppt[outliers_5sigma,"SID"],collapse = ",")))
      }      
    }
  }
}

```

```{r}


# 
# 
# for (coln in colnames(data_by_ppt)[2:ncol(data_by_ppt)]){
#   print(coln)
#   class(data_by_ppt[[coln]])
#   if(sum(is.na(data_by_ppt[[coln]]))<length(data_by_ppt[[coln]])){
#     hist(unlist(data_by_ppt[coln]),breaks=20,main = coln)
#   }
#   
# }
```

```{r}
#remove implausible TRSQ score
data_by_ppt$TRSQ[data_by_ppt$TRSQ<5]<-NA
```


```{r}
readr::write_csv(data_by_ppt, file = paste0(data_path,"data_by_ppt.csv"))


```

Should probably remove a few more outliers, and consider transforming non-normal data or using rank test for it, but that'll do for now.
### Exploratory analysis for health special issue

Here we'll follow a few basic steps:

 - Loop through each source and do these analyses. This might occur several times because we'll need to arrange different sources in unique ways.
 - Add each test of interest to a grand table of findings, storing the label, effect, and the p-value
 - Do FWE test on the findings to determine the end result


For each set, we'll need to loop through the three outcome measures, and then loop through the relevant predictor variables. We do two-way correlations to understand which should be followed up.



label the variables
```{r}
IVs <- c("SST_SSRT","SST_PostErrorSlowW1_median","SST_pes_mean_limited","ROC_Crave_Regulate_Minus_Look","ROC_Crave_Regulate",
         
         "SRHI_sum","SRHI_healthy_minus_unhealthy","TRSQ","RS","BIS_11",
         paste0("TESQ_E_",unique(scored_fs[scored_fs$scale_name=="TESQ_E","scored_scale"]))
         )
DVs <- c("cancer_promoting_minus_preventing_FFQ","FFQ_v2_Mean_Weighted_Nutrient_Density","FFQ_v2_Mean_Weighted_percent_daily_value","bf_1","bf_1_controlled")
```


Can we merge across surveys to only include the first survey taken? For each of these scales, participants may have only done a selection of the surveys

This would look like:

 - For each participant and column, merge across surveys and only include the FIRST result in each survey.
 

```{r}


#now we estimate R^2....
correlation_df <- data.frame()
for (DV in DVs){
  for(IV in IVs){
    #for (dn in draw_names){
      #pairwise_not_na <- (is.na(data_by_ppt %>% filter(survey_name==dn) %>% .[,IV])==FALSE) &  (is.na(data_by_ppt %>% filter(survey_name==dn) %>% .[,DV])==FALSE)
    pairwise_not_na <- (is.na(data_by_ppt %>% .[,IV])==FALSE) &  (is.na(data_by_ppt %>% .[,DV])==FALSE)
    if(sum(pairwise_not_na)>0){
      print(paste0(DV,",", IV, " (",as.character(sum(pairwise_not_na)) , " values)"))
        cor_res <-cor.test(
          #data_by_ppt %>% filter(survey_name==dn) %>% .[,IV],
          #data_by_ppt %>% filter(survey_name==dn) %>% .[,DV],
          data_by_ppt[[IV]],
          data_by_ppt[[DV]],
          use = "complete.obs"
        )
        #print(paste0("r value of ", as.character(cor_res$estimate)))
        cat(".")
        cor_df <- data.frame(
          "v1"=DV,
          "v2"=IV,
          "n"=sum(pairwise_not_na),
#          "survey"=dn,
          "statistic" = cor_res$statistic,
          "df" = cor_res$parameter,
          "p.value" = cor_res$p.value,
          "estimate"=cor_res$estimate,
          "ci_lower" = cor_res$conf.int[[1]],
          "ci_upper" = cor_res$conf.int[[2]]
          
          
        )
        correlation_df <-rbind(correlation_df,cor_df)
          #correlation_list <- correlation_list %>% add_stats(cor_res)
          

     # }#else{
        #print(paste("no valid column pair for:",IV,",", DV, " (",dn,")"))
      #}
   }
  }
}

#correlation_df <-  tidy_stats_to_data_frame(correlation_list)



```




```{r}
data_by_ppt %>% group_by(DEMO_mcarthur_social_standing) %>% summarise(mean_ffq=mean(cancer_promoting_minus_preventing_FFQ,na.rm=TRUE))

cor.test(data_by_ppt$DEMO_mcarthur_social_standing,data_by_ppt$cancer_promoting_minus_preventing_liked_FCI)
cor.test(data_by_ppt$DEMO_mcarthur_social_standing,data_by_ppt$cancer_promoting_minus_preventing_craved_FCI)
cor.test(data_by_ppt$DEMO_mcarthur_social_standing,data_by_ppt$cancer_promoting_minus_preventing_FFQ)
```


```{r}
ggplot(data_by_ppt,aes(DEMO_mcarthur_social_standing,data_by_ppt$cancer_promoting_minus_preventing_FFQ))+geom_point()
```




## Correlations


```{r, fig.width=26}
correlational_items <- c(IVs,DVs)

corrplot::corrplot(cor(data_by_ppt[,correlational_items],use = "pairwise.complete.obs"),
method="number",type="upper",diag=FALSE,tl.srt=35,tl.cex=0.8,cl.cex=0.8,number.cex=0.8,order="hclust")


```



```{r}
cor.test(data_by_ppt$SST_SSRT,data_by_ppt$bf_1)
cor.test(data_by_ppt$SST_SSRT,data_by_ppt$ROC_Crave_Minus_Neutral)
```




```{r}
cor.test(data_by_ppt$SST_SSRT,data_by_ppt$cancer_promoting_minus_preventing_FFQ)
cor.test(data_by_ppt$SST_SSRT,data_by_ppt$FFQ_v2_Mean_Weighted_Nutrient_Density)
cor.test(data_by_ppt$SST_SSRT,data_by_ppt$FFQ_v2_Mean_Dietary_Nutrient_Density)
```











