---
title: "sst_post_error_slowing"
output: html_notebook
---

Steps:

 - load file
 - number each trial consecutively based on the onset time
 - number the following trial for each trial
 - merge the file with itself, merging each trial with its following trial
 - for each measure the post-trial time for a correct result
 

 
 
 This paper probably has a good method, 'How to measure post-error slowing: A confound and a simple solution',
 
 Look at their "simple solution", and follow the method there. https://www.sciencedirect.com/science/article/abs/pii/S0022249612000454
 https://www.sciencedirect.com/science/article/pii/S0022249612000454
 
 https://www.frontiersin.org/articles/10.3389/fpsyg.2014.00119/full
 
 
 For the variables, see https://www.dropbox.com/scl/fi/acc3pmvb28b9swz0cnr82/Info-about-Stop-Signal-Task-Baseline-Analysis.docx?dl=0&rlkey=18mfzinj70pmuhdv8d00nh84e
 found in /Berkman Lab/Devaluation/Papers/Frontiers - Health Special Issue
 we should use: 
        PostErrorSlowW1_mean
        PostErrorSlowW1_median
not sst_pes_limited
 
 
## load file

```{r}
library(ggplot2)

```


```{r}
Sys.setenv(R_CONFIG_ACTIVE = Sys.info()["nodename"])
dropbox_file_dir = config::get("dev_analysis_data_dir")
sst_all_data_filepath <- "~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/sst_behavioral_data_all.csv"

sst_all_data_raw <- readr::read_csv(sst_all_data_filepath)

```
```{r}
library(dplyr)
```

 ## About the Stop Signal Task
 
Task format 
The participant must respond to an arrow stimulus, by selecting one of two options, depending on the direction in which the arrow points. If an audio tone is present, the subject must withhold making that response (inhibition). The test consists of two parts: In the first part, the participant is introduced to the test and told to select the left-hand button when they see a left-pointing arrow and the right-hand button when they see a right-pointing arrow. There is one block of 16 trials for the participant to practice this. In the second part, the participant is told to continue selecting the buttons when they see the arrows but, if they hear an auditory signal (a beep), they should withhold their response and not select the button. 
Go task (e.g. press left when an arrow pointing to the left appears, and right when an arrow pointing to the right appears) 
Stop signal (e.g. a cross replacing the arrow OR a tone?) appears after a variable stop-signal delay (SSD), instructing participants to suppress the imminent go response.  
Conceptualizes the ability to inhibit the response as a race between a Go- and a Stop process that are triggered by the presentation of the Go and Stop-signal, respectively. If the Go process finishes first, the response will be executed. If the Stop process finishes first, the response will be inhibited (Teichert, 2015).
Condition Type
 1 CorrectGo (i.e. pressed left when an arrow pointing to the left appears, and right when an arrow pointing to the right appears)
 2 FailedGo (i.e. did NOT press left when an arrow pointing to the left appears, and right when an arrow pointing to the right appears)
 3 CorrectStop (i.e. Suppressed the go response)
 4 FailedStop: (i.e. Failed to suppressed the go response)
 


### Calculate with respect to the pre-stop trial so that we can measure slowing/speeding in CS

We can be agnostic about it. simply record, for every trial where there is a reaction time before and after the trial, regardless of the trial type, what was the change?

First, we need to clean RTs
```{r}
sst_all_data<-sst_all_data_raw
sst_all_data$reaction_time_clean<-sst_all_data$reaction_time
sst_all_data$reaction_time_clean[sst_all_data$reaction_time==0]<-NA

hist(sst_all_data$reaction_time[sst_all_data$reaction_time>0.0])
hist(sst_all_data$reaction_time[(sst_all_data$reaction_time<0.3) & (sst_all_data$reaction_time>0.0)])

```

Based on eyeballing this histogram, reaction times start to increase around 0.2. So let's make the cut-off at 0.15. Less than that, and they aren't really a reaction.

```{r}
sst_all_data$reaction_time_clean[sst_all_data$reaction_time_clean<0.15]<-NA
```

```{r}
sst_all_data<- 
  sst_all_data %>% 
  mutate(has_response=!is.na(reaction_time_clean)) %>%
  mutate(follows_response_trial=lag(has_response,2),
         precedes_response_trial=lead(has_response,2)
         ) %>%
  mutate(post_pre_rt_change=lead(reaction_time_clean,2)-lag(reaction_time_clean,2))

#right. now we can view distributions of post_pre_rt_change by condition
ggplot(sst_all_data %>% filter(condition!="Cue"),
       aes(x=post_pre_rt_change,fill=condition))+
  geom_histogram()+facet_wrap(~condition,scales = "free")+
  geom_vline(xintercept=0)

for(cond in unique(sst_all_data$condition)){
  if(cond=="Cue"){next}
  print(cond)
  print("post minus pre trial reaction time change")
  sst_all_data_condition<-sst_all_data %>% filter(condition==cond)
  print(t.test(sst_all_data_condition$post_pre_rt_change))
}

#what about only if it's a trial preceded and followed by a CG trial?


```

This is kind of against my hypothesis. I thought that in CorrectStop trials, subjects would update that they have correct impulses in the trials and can therefore respond _faster_ in subsequent trials. But overall, they don't do that. Instead, after a correctstop trial, reaction time _increases_, probably because subjects use the trial as evidence of more Stop trials and therefore respond by slowing down.

However, it is possible that there is more than one evidential process happening, and they countervail.

We also know that the tone timing is adjusted. it isn't fixed; when the participants correctly stop in response to a tone, the tone delay is lengthened. When they fail to inhibit, the tone delay is shortened. So rational subjects also take that into account

In FailedStop trials, subjects increase their reaction times, by even more, because they want to avoid making an error. This can be seen as the compound of:

 - the fact of a stop trial increases evidence that stop trials occur and subjects should be prepared for them, DELAYING reaction time
 - response was punished and subjects update against the possibility of a response given the evidence they were presented in by raising the evidence threshold/lowering the pre-potent response, DELAYING reaction time.
 - On the other hand, tone delay is shortened in these cases, to make the task easier (runSST.m line 730), and rational subjects would actually wait less in response to that, DECREASING reaction time
 
Overall, subjects respond to a Failed
 
 so in CS trials, you have

- the fact of a stop trial increases evidence that stop trials occur and subjects should be prepared for them, DELAYING reaction time
- tone delay is lengthened, to make the task more difficult (runSST.m line 748), and rational subjects would therefore wait longer before pressing the button, DELAYING reaction time

but you do not have a punished response.

in CG trials:

 - evidence that Stop trials occur decreases, DECREASING reaction time
 - reward of Go response occurs, DECREASING raction time

No tone delay change in these trials.

In FG trials:
 - punishment of no go occurs, DECREASING reaction time

So when calculating when it is rational to respond, you need to consider:
 - prior probability that a trial is a stop trial
 - prior probability, given a certain amount of evidence accumulated, that the trial is a stop trial
 - adjustment of the tone delay

Together these three factors could predict behavior.

This model might need revision if it turns out participants are told in advance that the amount of Correct Stop trials will match the amount of Failed Stop trials. I don't think they are.

Let's calculate this. First, the prior probability that a trial is a stop trial, given all the evidence gathered by the participant:

```{r}

sst_all_data <- sst_all_data %>% group_by(subid,waveid,runid) %>%
  mutate(
    CumulativeGoTrials=cumsum(go_no_go_condition_label=="Go"),
    CumulativeStopTrials=cumsum(go_no_go_condition_label=="Stop")
  ) %>% mutate(
    PP_IsGo=(lag(CumulativeGoTrials,2)/
      (lag(CumulativeGoTrials,2)+lag(CumulativeStopTrials,2))
    ),
    PP_IsStop=(lag(CumulativeStopTrials,2)/
      (lag(CumulativeGoTrials,2)+lag(CumulativeStopTrials,2))
    )
  )
    
#table(sst_all_data$go_no_go_condition_label,sst_all_data$condition)

#sst_all_data %>% select(subid,waveid,trial_number,go_no_go_condition_label,condition,CumulativeGoTrials,CumulativeStopTrials,PP_IsGo,PP_IsStop)

```

Then we have subjective uncertainty around when a tone occurs, given that we are in a stop trial and a tone will occur $P(t_o|S)$. Let's say it's a normal distribution with mean $\mu_t$, sd $\sigma_t$, $N(\mu_t,\sigma_t)$. Given $\mu_t$ and $\sigma_t$, we calculate the probability, given we're in a stop trial, of a tone occuring as modeled by that normal distribution, $P(T_t|S)=N(\mu_t,\sigma_t)$. Combined with the prior probability of a tone occuring, $P(S)$, we can calculate the posterior likelihood of $P(S)$ as:

$$
P(S|T_t)=\frac{P(~T_t|S) P(S)}{P(~T_t)}

$$
where $P(~T_t)$ is 1 while no tone occurs, then 0.

$\mu_t$ will be the past observations of tone times, while $\sigma_t$ is the subjective error in perception of tone delay; uncertain how to quantify this but we could make it $\sigma_t=0.15\text{ s}$ to start.

More generally $\mu_t$ would be some function of all the past tone times, somewhere between an average of all of them, and the latest tone time. As a compromise let's define it as the average of each.

Then let's define our $\mu_t$ as


```{r}
lag(1:10,2)
sst_all_data[,c("trial_duration","condition")]
sst_all_data$last_tone_delay<-NA
sst_all_data <-sst_all_data %>% group_by(subid,waveid,runid) %>%
  mutate(
    last_tone_delay=case_when(
      lag(SSD_recorded,1)>0 ~lag(SSD_recorded,1),
      TRUE ~ as.numeric(NA)
    )
  ) %>%
  tidyr::fill(last_tone_delay,.direction="down")

sst_all_data <- sst_all_data %>% group_by(subid,waveid,runid) %>%
  mutate(SSD_event_prior = lag(SSD_recorded,1)>0) %>%
  mutate(lagged_tone_delay = lag(SSD_recorded,1)) %>%
  mutate(average_tone_delay = (
    cumsum(ifelse(is.na(lagged_tone_delay),0,lagged_tone_delay))/
      cumsum(ifelse(is.na(SSD_event_prior),0,SSD_event_prior))
  ))
  




#sst_all_data$expected_tone_delay<-rowMeans(sst_all_data[,c("last_tone_delay", "average_tone_delay")])
#probably more rational, given what the task actually is, and also easier
sst_all_data$expected_tone_delay<-sst_all_data$last_tone_delay


```


***so perhaps we can predict putamen activity by the combination of $P(~T_t)$ and $P(T_t|S)=N(\mu_t,\sigma_t)$, or simpler representations of derivatives thereof. maybe just a linear model of....***

So, we:

 - assume the putamen signal is a kind of `readiness potential'
 - Take eitehr the map in this contrast, or the region, and model its activity as a function of $P(\neg T_t)$ and $\mu_t$ from $P(T_t|S)=N(\mu_t,\sigma_t)$. I am a bit sceptical because we haven't seen anything in reaction time, so I'm not sure why these would do better...
 The baseline would be just to model the region as a function of following a correctstop vs. a failedstop vs. a correctgo. It would be affirmed if the correlation between our model variables and activity is better than the biserial correlation of correctstop vs. failedstop alone.
 If this model is correct, we would also expect CG following (correctgo vs. failed stop) to show even more putamen activity than merely correctstop vs. failedstop--because there's more relative readiness potential. If we found _less_, that would suggest the putamen activity comes from some kind of affirmation of task ability derived from the fact that the participant correctly stopped, i.e., RPE is somehow larger in CorrectStop compared to CorrectGo. Go trials make up 83% of all trials; of those 70% points are correct and the remaining 13% are incorrect--(16% of all Go trials). Stop trials make up 15% of of all trials, of which 12% are correct and 3% are incorrect (20% of all Go trials). So actually, Stop trials are not 'harder', they're experienced as about equally challenging. However there are fewer stop trials; participants might be less confident about their performance on those trials, and as a result, performing well on them could be more rewarding. There's also some kind of cognitive explanation I keep trying to put my finger on: getting a Stop trial correct affirms that the participant can successfully withhold a response, and they have had much less confirmation of their own ability to do that successfully than their ability to get a Go trial correct, so it might be more rewarding on that basis. Crucially, also confirms that they don't have to slow down on the subsequent trial, which is why we see fairly minor slowing following a CS trial (I wonder what the expected tone delay change is for CS compared to FS?).
 
Simplest explanation might just be: Go response punishment [internal penalty] follows a FS trial, whereas NoGo inhibition reward follows a CS trial. The punishment is enough to inhibit putamen response.

I really want to do that sample of activity right from the point the subject learns they were right or wrong. So we get the timing of every single trial, synhronize, and graph the succession of responses using a moving average following FS, CS, FG, CG.

```{r}

sst_all_data<- 
  sst_all_data %>% 
  #mutate(has_response=!is.na(reaction_time_clean)) %>%
  # mutate(follows_response_trial=lag(has_response,2),
  #        precedes_response_trial=lead(has_response,2)
  #        ) %>%
  mutate(post_pre_E_t_delay_change=lead(expected_tone_delay,2)-lag(expected_tone_delay,2))

#right. now we can view distributions of post_pre_rt_change by condition
ggplot(sst_all_data %>% filter(condition!="Cue"),
       aes(x=post_pre_E_t_delay_change,fill=condition))+
  geom_histogram()+facet_wrap(~condition,scales = "free")+
  geom_vline(xintercept=0)

for(cond in unique(sst_all_data$condition)){
  if(cond=="Cue"){next}
  print(cond)
  print("post minus pre trial reaction time change")
  sst_all_data_condition<-sst_all_data %>% filter(condition==cond)
  print(t.test(sst_all_data_condition$post_pre_E_t_delay_change))
}

#what about only if it's a trial preceded and followed by a CG trial?


```



 

## empirical distribution of P_S_given_T_at_rt

Now we know all this, we could calculate $P(S|~T_t)$, but what $t$ do we want to know about? perhaps we could calculate the expected probability of a tone at the instant the subject presses a button, when they press it. This would be....

```{r}
#let's add time for the participant to actually move
sst_all_data$P_T_at_rt_given_S<-1-pnorm(sst_all_data$reaction_time_clean-0.1,sst_all_data$expected_tone_delay,0.15)
#then the prior probability of S
sst_all_data$P_S_given_T_at_rt<-sst_all_data$PP_IsStop*sst_all_data$P_T_at_rt_given_S

hist(sst_all_data$P_S_given_T_at_rt,breaks = 100)
hist(log(sst_all_data$P_S_given_T_at_rt,10),breaks=100)
hist(log(sst_all_data$P_S_given_T_at_rt,10),breaks=100)
```




## empirical distribution of P_S_given_T_at_tone

We can also calculate the probability of a tone at the instant the subject hears it....

```{r}
#let's add time for the participant to actually move
sst_all_data$P_T_at_tone_given_S<-1-pnorm(sst_all_data$SSD_recorded,sst_all_data$expected_tone_delay,0.15)
#then the prior probability of S
sst_all_data$P_S_given_T_at_tone<-sst_all_data$PP_IsStop*sst_all_data$P_T_at_tone_given_S

hist(sst_all_data$P_S_given_T_at_tone,breaks=100)
hist(log(sst_all_data$P_S_given_T_at_tone,10))
```

### learning rate


Bernice suggests: subjects differ from rationality in a couple of different ways

These might be the learning rate $P(S)$ and $P(\neg T_t|S)$

### can we model this?

So that looks like an exponential distribution...could also be modeled as Gamma or weibull...

```{r}
alpha<- mean(sst_all_data$P_S_given_T_at_rt,na.rm = TRUE)^2/var(sst_all_data$P_S_given_T_at_rt,na.rm = TRUE)
beta<- var(sst_all_data$P_S_given_T_at_rt,na.rm = TRUE)/mean(sst_all_data$P_S_given_T_at_rt,na.rm = TRUE)

x<-(1:1000)/1000
plot(x,dgamma(x,alpha/8,beta))
```

```{r}
x_vec<-sst_all_data$P_S_given_T_at_rt[!is.na(sst_all_data$P_S_given_T_at_rt)]
library(MASS)

res<-fitdistr(x_vec, dgamma, start=list(shape=1, scale=1))
plot(x,dgamma(x,res[[1]][[1]],scale=res[[1]][[2]]))
```

```{r}
res<-fitdistr(x_vec, dexp, start=list(rate=1))
plot(x,dgamma(x,res[[2]][[1]]))
```


```{r}
dexp(c(0.1,0.5,0.9),1)
```

### different tack, transform back to normal????

```{r}

hist(log(sst_all_data$P_S_given_T_at_rt,10),100)

hist(log(-log(sst_all_data$P_S_given_T_at_rt,10)),100)

#yeah this is very messy.
print(mean(log(-log(sst_all_data$P_S_given_T_at_rt,10)),na.rm = TRUE))
print(sd(log(-log(sst_all_data$P_S_given_T_at_rt,10)),na.rm = TRUE))



```





So at that point, when the subject hears a tone, they will move quickly from the prior probability to near-certainty that this is a stop trial (because they have heard the tone).

# Within subject

How much variance is within-subject vs. between-subject? And do subjects change their probability thresholds over time?


```{r}
#across-subject variance
sst_all_data$P_S_given_T_at_rt
```


# Figuring out the SSD definitions...

```{r}
table(sst_all_data$SSD_technical)
table(sst_all_data$SSD_observed)
table(sst_all_data$condition, sst_all_data$SSD_recorded>0)
table(sst_all_data$condition, sst_all_data$SSD_recorded>0)
```

```{r}
sst_all_data[sst_all_data$condition=="FailedStop",]
```

```{r}

sst_all_data[sst_all_data$condition=="FailedStop",c("ladder_number","LadderX_SSD_ms","SSD_recorded", "reaction_time")]
```

```{r}
sst_all_data$ReactionBeforeLadderScheduled<-sst_all_data$reaction_time<sst_all_data$LadderX_SSD_ms/1000
sst_all_data[sst_all_data$condition=="FailedStop" & sst_all_data$SSD_recorded==0,c("ladder_number","LadderX_SSD_ms","SSD_recorded", "reaction_time","condition","ReactionBeforeLadderScheduled")]
```

Okay, so LadderX_SSD_ms is actually the planned SSD. For the few Stop trials where there is no stop signal (I don't know why this happens!) we can look at LadderX_SSD_ms to figure out what it should have been.


```{r}
sst_rtgt0<-sst_all_data[sst_all_data$reaction_time>0,]
table(sst_rtgt0$condition, sst_rtgt0$SSD_recorded>0,sst_rtgt0$ReactionBeforeLadderScheduled)
```

```{r}
plot(sst_all_data$LadderX_SSD_ms,sst_all_data$SSD_recorded)
```




