---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 4
---

To run this script: 1. Download HINTS 5 datasets from <https://hints.cancer.gov/view-questions-topics/all-hints-questions.aspx> to your data folder. Download all cycles of the data. 2. In the data folder, unzip each dataset. 3. Change the location parameter for the `get_hints5` call in the block below to point to your data folder. 4. Run this script.

```{r message=FALSE, warning=FALSE}
Sys.setenv(R_CONFIG_ACTIVE = Sys.info()["nodename"])

library(dplyr)
library(lavaan)
library(mediation)
source("HINTS_preprocessing.R")
source("orfcs_utilities.R")
source("gen_utilities.R")
hints5 <-get_hints5(location=config::get("hints_protected_data_folderpath"))
hints5$HINTSIsRural[grepl("Not coded",hints5$PR_RUCA_2010)]<-NA
hints5$HINTSIsRural_i[grepl("Not coded",hints5$PR_RUCA_2010)]<-NA

boot_times<-10000

zscore <- function(x){
    return((x-mean(x,na.rm=TRUE))/sd(x,na.rm=TRUE))
}
```

```{r}
# table(orfcs_dataset$RuralZIP_i,
#       orfcs_dataset$Gender3C,
#       orfcs_dataset$RaceCategorical=="HispanicAnyRace"
#       )
```

```{r}
sapply(c("Metropolitan", "Micropolitan", "Small town", "Rural"),
       function(cat){sum(grepl(cat,hints5$PR_RUCA_2010))}
       )
```

what's the variability between men and women

including exercise or energy expenditure

exercise can improve objective health without/before it changes BMI.

weight physical activity and food intake

low income women, particularly low income women head of households, are of particular concern, and possibly hispanic women

```{r}
#table(orfcs_dataset$RuralZIP_i,
#      orfcs_dataset$Gender3C,
#      orfcs_dataset$RaceCategorical=="HispanicAnyRace"
#      )
```


```{r}
table(hints5$GeneralHealth_of) %>% cumsum / sum(!is.na(hints5$GeneralHealth_of))

hist(as.integer(hints5$GeneralHealth_of))
```

```{r}
library(magrittr)
library(dplyr)



data_dir <- config::get("rural_data_dir")

preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed2_anon_by_subj.csv")
library(readr)
library(ggplot2)
library(GGally)
orfcs_dataset <- readr::read_csv(preprocessed_data_filepath)



```

Let's do our best to include all the same covariates we previously included.

# Prep

```{r}
library(stringi)
# [1] "Fruit_vegetables_z~HINTSIsRural_i+Age_c+I(Age_c^2)+RacePP+Gender3C+filename"
# [1] "MedConditions_HighBP_i~Fruit_vegetables_z+HINTSIsRural_i+Age_c+I(Age_c^2)+RacePP+Gender3C+filename"
# IncomeRanges_r

#need to do prepare variables so lavaan can process them
hints5_pp <- hints5
#add quadratic
hints5_pp$Age_c_pow2 <- hints5_pp$Age_c^2


#one-hot some variables
factor_to_clean_string <- function(data, col_to_stringify){
  data[[col_to_stringify]] <- as.character(data[[col_to_stringify]])
  data[[col_to_stringify]] <- (
    str_replace_all(data[[col_to_stringify]],"\\s","_") %>% 
      str_replace_all("\\W","")
  )#table(hints5_pp[[col_to_stringify]])
  return(data)
}

hints5_pp<-factor_to_clean_string(hints5_pp,"RacePP2")
hints5_pp$RacePP2<-factor(hints5_pp$RacePP2)
hints5_pp <- mltools::one_hot(hints5_pp,"RacePP2",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("RacePP2_",colnames(hints5_pp))],collapse=" + "))

hints5_pp<-factor_to_clean_string(hints5_pp,"Hisp_Cat2")
hints5_pp$Hisp_Cat2<-factor(hints5_pp$Hisp_Cat2,levels=names(sort(table(hints5_pp$Hisp_Cat2),decreasing = TRUE)))
hints5_pp <- mltools::one_hot(hints5_pp,"Hisp_Cat2",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("Hisp_Cat2_",colnames(hints5_pp))],collapse=" + "))

hints5_pp<-factor_to_clean_string(hints5_pp,"Gender3C")
hints5_pp$Gender3C<-factor(hints5_pp$Gender3C)
hints5_pp <- mltools::one_hot(hints5_pp,"Gender3C",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("Gender3C_",colnames(hints5_pp))],collapse=" + "))



```

Now prepare the ORFCS dataset for lavaan.

```{r}
#need to do prepare variables so lavaan can process them
orfcs_dataset_pp <- data.table(orfcs_dataset)
#add quadratic
orfcs_dataset_pp$DEMO_Age_c_pow2 <- orfcs_dataset_pp$DEMO_Age_c^2


#one-hot some variables


orfcs_dataset_pp<-factor_to_clean_string(orfcs_dataset_pp,"RaceC2")
orfcs_dataset_pp$RaceC2<-factor(orfcs_dataset_pp$RaceC2)
orfcs_dataset_pp <- mltools::one_hot(orfcs_dataset_pp,"RaceC2",dropCols = FALSE)
print(paste0(colnames(orfcs_dataset_pp)[grepl("RaceC2_",colnames(orfcs_dataset_pp))],collapse=" + "))

orfcs_dataset_pp<-factor_to_clean_string(orfcs_dataset_pp,"Gender3C")
orfcs_dataset_pp$Gender3C<-factor(orfcs_dataset_pp$Gender3C)
orfcs_dataset_pp <- mltools::one_hot(orfcs_dataset_pp,"Gender3C",dropCols = FALSE)
print(paste0(colnames(orfcs_dataset_pp)[grepl("Gender3C_",colnames(orfcs_dataset_pp))],collapse=" + "))
```

# Descriptive statistics

```{r}

ffq_fv_cor <- cor.test(orfcs_dataset_pp$FFQ_fruit_vegetables_z,orfcs_dataset_pp$cancer_promoting_minus_preventing_FFQ_z)
print(ffq_fv_cor)
print(ffq_fv_cor$conf.int)

```

# Oregon dataset: basic disparity

# HINTS dataset: two mediators

This follows Hayes PROCESS Model 6 with two mediators but we are doing it here in Lavaan.

Variables are:

-   Treatment: Rurality
-   Two Mediators: household income, and fruit and vegetable consumption, in that order.
-   Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure. (and cancer??)

This model below is adapted from <https://towardsdatascience.com/doing-and-reporting-a-serial-mediation-model-with-two-mediators-in-r-with-lavaan-739ed3155814>

I think they've left some things out. I need to do a bit more research to work out how to properly implement this, probably including a basic crash course in SEM.

For the basic HINTs lms, see `HINTS_health_outcomes.Rmd`.

```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
hints_model_template=
"
  #Regressions
  IncomeRanges_r ~ ab*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  Fruit_vegetables_z ~ bc*IncomeRanges_r + ac*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  (OUTCOMEVAR) ~ cd*Fruit_vegetables_z + bd*IncomeRanges_r + ad*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  
  #Defined Parameters:
  indirect_effect := ab*bc*cd
  effect_via_inc_only :=ab*bd
  effect_via_fruit_vege_only :=ac*cd
  direct_effect := ad
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI",
  "GeneralHealth_i",
  "MedConditionsAggregate",
  "MedConditions_HighBP_i",
  "EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```

```{r}



hints_fits_by_outcome<- list()

for (outcome_var in outcome_measures){
  set.seed(05711846)
  hints_model_w_outcome <- str_replace_all(hints_model_template,"\\(OUTCOMEVAR\\)",outcome_var)
  cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
  cat(hints_model_w_outcome)
  fit=sem(
    hints_model_w_outcome,
    hints5_pp,
    se = "bootstrap",
    bootstrap=boot_times,
    likelihood = "wishart")
  
  hints_fits_by_outcome[[outcome_var]]<-fit
  print(summary(fit,ci=TRUE))
  cat("-----\n\n\n")
}
```



```{r}
# 
# set.seed(05711846)
# 
# fit=sem(
#   hints_model,
#   hints5_pp,
#   se = "bootstrap",
#   bootstrap=1000,
#   likelihood = "wishart")
# summary(fit)
```
## with interaction terms

see https://rpubs.com/alliechoate/502710
```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
hints_model_template_int=
"
  #Regressions
  IncomeRanges_r ~ ab*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  Fruit_vegetables_z ~ bc*IncomeRanges_r + ac*HINTSIsRural_i + bc_g*IncomeRanges_r:HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  (OUTCOMEVAR) ~ cd*Fruit_vegetables_z + bd*IncomeRanges_r + ad*HINTSIsRural_i + cd_g*Fruit_vegetables_z:HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  
  #Defined Parameters:
  indirect_effect_ctrl := ab*bc*cd
  indirect_effect_treat := ab*(bc+bc_g)*(cd+cd_g)
  indirect_effect_avg := (ab*bc*cd + ab*(bc+bc_g)*(cd+cd_g))/2
  indirect_effect_diff := ab*bc*cd - ab*(bc+bc_g)*(cd+cd_g)
  effect_via_inc_only :=ab*bd
  effect_via_fruit_vege_only :=ac*cd
  direct_effect := ad
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI",
  "GeneralHealth_i",
  "MedConditionsAggregate", #would benefit from being modelled as a poisson or something.x`
  "MedConditions_HighBP_i",
  "EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```

## even more interaction terms

see https://rpubs.com/alliechoate/502710
```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
hints_model_template_int=
"
  #Regressions
  IncomeRanges_r ~ ab*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  Fruit_vegetables_z ~ bc*IncomeRanges_r + ac*HINTSIsRural_i + bc_g*IncomeRanges_r:HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  (OUTCOMEVAR) ~ cd*Fruit_vegetables_z + bd*IncomeRanges_r + ad*HINTSIsRural_i + cd_g*Fruit_vegetables_z:HINTSIsRural_i + bd_g*IncomeRanges_r:HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  
  #Defined Parameters:
  indirect_effect_ctrl := ab*bc*cd
  indirect_effect_treat := ab*(bc+bc_g)*(cd+cd_g)
  indirect_effect_avg := (ab*bc*cd + ab*(bc+bc_g)*(cd+cd_g))/2
  indirect_effect_diff := ab*bc*cd - ab*(bc+bc_g)*(cd+cd_g)
  effect_via_inc_only :=ab*bd
  effect_via_fruit_vege_only :=ac*cd
  direct_effect := ad
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI",
  "GeneralHealth_i",
  "MedConditionsAggregate", #would benefit from being modelled as a poisson or something.x`
  "MedConditions_HighBP_i",
  "EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```


```{r}



hints_fits_by_outcome_int<- list()

for (outcome_var in outcome_measures){
  set.seed(05711846)
  hints_model_w_outcome <- str_replace_all(hints_model_template_int,"\\(OUTCOMEVAR\\)",outcome_var)
  cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
  cat(hints_model_w_outcome)
  fit=sem(
    hints_model_w_outcome,
    hints5_pp,
    se = "bootstrap",
    bootstrap=boot_times,
    likelihood = "wishart",
    )
  
  hints_fits_by_outcome_int[[outcome_var]]<-fit
  print(summary(fit,ci=TRUE))
  cat("-----\n\n\n")
}
```


# Oregon dataset: 

## As pre-registered

Here, we replicate the model run in study_1_results.Rmd. To show progression from one model to the next, let's try to do everything here in lavaan.


```{r}


#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


# [1] "RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported + RaceC2_WhiteOnly"
# [1] "Gender3C_Female + Gender3C_Male + Gender3C_Other"

# mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
# mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
oregon_model_template="  
  MESA_healthyfoodavailability_z ~ ab*RuralZIP_i + DEMO_Age_c + Gender3C_Male + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported + PSS_z
  
  (OUTCOMEVAR) ~ bc*MESA_healthyfoodavailability_z + ac*RuralZIP_i + DEMO_Age_c + Gender3C_Male + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported + PSS_z
  
  
  #Defined Parameters:
  indirect_effect := ab*bc
  direct_effect := ac
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI"#,
  #"GeneralHealth_i",
  #"MedConditionsAggregate",
  #"MedConditions_HighBP_i",
  #"EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```



```{r}


#filter out male and female subjects
orfcs_dataset_pp_2g<-orfcs_dataset_pp %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))


# for (outcome_var in outcome_measures){
set.seed(8233042)
outcome_var <- "BMI"
oregon_model_w_outcome <- str_replace_all(oregon_model_template,"\\(OUTCOMEVAR\\)",outcome_var)
cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
cat(oregon_model_w_outcome)
orfcs_fit=sem(
  oregon_model_w_outcome,
  orfcs_dataset_pp_2g,
  se = "bootstrap",
  bootstrap=boot_times#,
  #likelihood = "wishart"
  )

summary(orfcs_fit,ci=TRUE)
  # cat("-----\n\n\n")
# }


#install.packages("semhelpinghands")
library(semhelpinghands)
boot_ci<-standardizedSolution_boot_ci(orfcs_fit)

boot_ci[boot_ci$label=="indirect_effect",]
orfcs_fit_boot <- extract_and_label_bootstrap_results(orfcs_fit)

ab_bc <- orfcs_fit_boot[,1]*orfcs_fit_boot[,2]
# print(quantile(ab_bc,c(.025,.975)))
# library(bootstrap)
# bcanon(ab_bc,200,mean,alpha=c(0.025,0.975))


```



OK this hasn't quite worked out. I think it's the CIs that are calculated in lavaan diffrently to mediation package. It can't meerely be the BCA, becuase ven with out the BCA, the mediate model still has about the same CI. It also isn't the sample, because I've got these down to be testing exactly the same sample of participants.


```{r}
set.seed(6472426)

mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,orfcs_dataset_pp_2g)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,orfcs_dataset_pp_2g)

mediate_result <- mediate(mb,mc,sims=boot_times, boot=TRUE,boot.ci.type = "bca", treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
summary(mb)
summary(mc)


```

```{r}
library(mediation)
mediate_result <- mediate(mb,mc,sims=boot_times, treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
summary(mc)
```

## three mediators

For comparison with HINTS, we'll first repeat the HINTS dataset two-mediator model as described above, but using three mediators.

Then, we'll proceed with our main Oregon dataset analysis.

This follows Hayes PROCESS Model 6 with THREE mediators but we are doing it here in Lavaan.

Variables are:

-   Treatment: Rurality
-   Two Mediators: household income, MESA healthy food availability, and fruit and vegetable consumption, in that order.
-   Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


# mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
# mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

# [1] "RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported + RaceC2_WhiteOnly"
# [1] "Gender3C_Female + Gender3C_Male + Gender3C_Other"

#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
oregon_model_template=
"
  #Regressions
  aSES_02_z ~ ab*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  MESA_healthyfoodavailability_z ~ bc*aSES_02_z + ac*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  FFQ_fruit_vegetables_z ~ cd*MESA_healthyfoodavailability_z + bd*aSES_02_z + ad*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  (OUTCOMEVAR) ~ de*FFQ_fruit_vegetables_z + ce*MESA_healthyfoodavailability_z + be*aSES_02_z + ae*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  
  #Defined Parameters:
  indirect_effect := ab*bc*cd*de
  effect_via_food := ac*cd*de
  effect_via_income := ab*be
  effect_via_inc_eating := ab*bd*de
  effect_via_eating := ad*de
  direct_effect := ae
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI"#,
  #"GeneralHealth_i",
  #"MedConditionsAggregate",
  #"MedConditions_HighBP_i",
  #"EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```

```{r}




# for (outcome_var in outcome_measures){
set.seed(8233042)
outcome_var <- "BMI"
oregon_model_w_outcome <- str_replace_all(oregon_model_template,"\\(OUTCOMEVAR\\)",outcome_var)
cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
cat(oregon_model_w_outcome)
orfcs_fit=sem(
  oregon_model_w_outcome,
  orfcs_dataset_pp,
  se = "bootstrap",
  bootstrap=boot_times,
  likelihood = "wishart")

summary(orfcs_fit,ci=TRUE)
  # cat("-----\n\n\n")
# }


```


### with interaction term



```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


# mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
# mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

# [1] "RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported + RaceC2_WhiteOnly"
# [1] "Gender3C_Female + Gender3C_Male + Gender3C_Other"

#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
oregon_model_template_int=
"
  #Regressions
  aSES_02_z ~ ab*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  MESA_healthyfoodavailability_z ~ bc*aSES_02_z + ac*RuralZIP_i + bc_g*RuralZIP_i:aSES_02_z + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  FFQ_fruit_vegetables_z ~ cd*MESA_healthyfoodavailability_z + bd*aSES_02_z + ad*RuralZIP_i + cd_g*RuralZIP_i:MESA_healthyfoodavailability_z + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  (OUTCOMEVAR) ~ de*FFQ_fruit_vegetables_z + ce*MESA_healthyfoodavailability_z + be*aSES_02_z + ae*RuralZIP_i + de_g*RuralZIP_i:FFQ_fruit_vegetables_z + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  
  #Defined Parameters:
  indirect_effect_ctrl := ab*bc*cd*de
  indirect_effect_treat := ab*(bc+bc_g)*(cd+cd_g)*(de+de_g)
  # indirect_effect_avg := (ab*bc*cd*de + ab*(bc+bc_g)*(cd+cd_g)*(de+de_g))/2
  # indirect_effect_diff := ab*(bc+bc_g)*(cd+cd_g)*(de+de_g) - ab*bc*cd*de
  # model didn't work with these included.
  
  effect_via_food := ac*cd*de
  effect_via_income := ab*be
  effect_via_inc_eating := ab*bd*de
  effect_via_eating := ad*de
  direct_effect := ae
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI"#,
  #"GeneralHealth_i",
  #"MedConditionsAggregate",
  #"MedConditions_HighBP_i",
  #"EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```

### even more interaction terms



```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


# mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
# mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

# [1] "RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported + RaceC2_WhiteOnly"
# [1] "Gender3C_Female + Gender3C_Male + Gender3C_Other"

#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
oregon_model_template_int=
"
  #Regressions
  aSES_02_z ~ ab*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  MESA_healthyfoodavailability_z ~ bc*aSES_02_z + ac*RuralZIP_i + bc_g*RuralZIP_i:aSES_02_z + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  FFQ_fruit_vegetables_z ~ cd*MESA_healthyfoodavailability_z + bd*aSES_02_z + ad*RuralZIP_i + cd_g*RuralZIP_i:MESA_healthyfoodavailability_z + bd_g*aSES_02_z:RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  (OUTCOMEVAR) ~ de*FFQ_fruit_vegetables_z + ce*MESA_healthyfoodavailability_z + be*aSES_02_z + ae*RuralZIP_i + de_g*RuralZIP_i:FFQ_fruit_vegetables_z + ce_g*RuralZIP_i:MESA_healthyfoodavailability_z + be_g*RuralZIP_i:MESA_healthyfoodavailability_z + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  
  #Defined Parameters:
  indirect_effect_ctrl := ab*bc*cd*de
  indirect_effect_treat := ab*(bc+bc_g)*(cd+cd_g)*(de+de_g)
  # indirect_effect_avg := (ab*bc*cd*de + ab*(bc+bc_g)*(cd+cd_g)*(de+de_g))/2
  # indirect_effect_diff := ab*(bc+bc_g)*(cd+cd_g)*(de+de_g) - ab*bc*cd*de
  # model didn't work with these included.
  
  effect_via_food := ac*cd*de
  effect_via_income := ab*be
  effect_via_inc_eating := ab*bd*de
  effect_via_eating := ad*de
  direct_effect := ae
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI"#,
  #"GeneralHealth_i",
  #"MedConditionsAggregate",
  #"MedConditions_HighBP_i",
  #"EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```


```{r}




# for (outcome_var in outcome_measures){
set.seed(8233042)
outcome_var <- "BMI"
oregon_model_w_outcome <- str_replace_all(oregon_model_template_int,"\\(OUTCOMEVAR\\)",outcome_var)
cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
cat(oregon_model_w_outcome)
orfcs_fit_int=sem(
  oregon_model_w_outcome,
  orfcs_dataset_pp,
  se = "bootstrap",
  bootstrap=boot_times,
  likelihood = "wishart")

summary(orfcs_fit_int,ci=TRUE)
  # cat("-----\n\n\n")
# }


```



# Hybrid: three mediators

This follows Hayes PROCESS Model 6 with THREE mediators. We need to somehow manually combine the two datasets by multiplying effects. Need to follow bootstrap analysis, which means we need to extract raw bootstrap results and combine them. I'm not sure it's feasible, but it would be quite valuable to do.

Variables are:

-   Treatment: Rurality
-   Two Mediators: household income, MESA healthy food availability, and fruit and vegetable consumption, in that order.
-   Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

## Hybrid Analysis run

```{r}
get_fit_PE<-function(fit_to_read){
  sink("temp_out.txt")
  fit_pe<-summary(fit_to_read,ci=TRUE)$pe
  sink(NULL)
  return(fit_pe)
}

lavaan_results_list <- list()
for (hints_fit_label in names(hints_fits_by_outcome)){
  hints_fit<-hints_fits_by_outcome[[hints_fit_label]]
  lavaan_summarized_results <- get_fit_PE(hints_fit) %>% filter(label!="")
  lavaan_summarized_results[["outcome"]]<-hints_fit_label
  lavaan_results_list<-append(lavaan_results_list,list(lavaan_summarized_results))
}
lavaan_results_df <- do.call(rbind,lavaan_results_list)
```


```{r, warning=FALSE}



orfcs_boot<-extract_and_label_bootstrap_results(orfcs_fit)
colnames(orfcs_boot)<-
  paste0("orfcs_",colnames(orfcs_boot))

#raw_data_list<-list()

hybrid_effect_list <-list()
for (effect_name in names(hints_fits_by_outcome)){
  cat(paste0("HYBRID INDIRECT EFFECT FOR: ",effect_name,"\n\n"))
  hints_boot <-extract_and_label_bootstrap_results(hints_fits_by_outcome[[effect_name]])
  # sink("temp_diversion.txt")
  # lavaan_computed_indirect_effect <- (
  #   summary(hints_fits_by_outcome[[effect_name]])$PE %>% filter(label=="indirect_effect")
  # )
  # sink(NULL)
  colnames(hints_boot)<-
    paste0("hints_",colnames(hints_boot))
  
  
  row_count <- min(nrow(orfcs_boot),nrow(hints_boot))
  combined_boot_results <- data.frame(cbind(orfcs_boot[1:row_count,],hints_boot[1:row_count,]))
  
  #raw_data_list[[effect_name]]<-combined_boot_results
  
  # cat("HINTS lavaan pre-computed indirect effect:\n")
  # cat(paste(names(lavaan_computed_indirect_effect),collapse="\t"))
  # cat(paste(lavaan_computed_indirect_effect,collapse="\t"))
  # 
  # cat("\n")

  cat("HINTS indirect effect:\n ")  
  HINTS_indirect_effect <- apply(combined_boot_results %>% dplyr::select(hints_ab, hints_bc, hints_cd),1,prod)
  summarize_calculated_effect(HINTS_indirect_effect)
  
  cat("HINTS direct effect:\n ")  
  HINTS_direct_effect <- combined_boot_results$hints_ad
  hie_result<- summarize_calculated_effect(HINTS_direct_effect)
  hybrid_effect_set<-list("indirect_effect"=hie_result)
  
  cat("Hybrid indirect effect:\n ")
  hybrid_main_indirect_effect <- apply(combined_boot_results %>% dplyr::select(hints_ab, orfcs_bc,orfcs_cd, hints_cd),1,prod)
  hie_result <- summarize_calculated_effect(hybrid_main_indirect_effect)
  hybrid_effect_set<-list("indirect_effect"=hie_result)
  
  cat("Hybrid effect via food availability and consumption:\n ")
  hybrid_indirect_effect1 <- apply(combined_boot_results %>% dplyr::select(orfcs_ac,orfcs_cd, hints_cd),1,prod)
  hie_result <- summarize_calculated_effect(hybrid_indirect_effect1)
  hybrid_effect_set <- append(hybrid_effect_set,list("availability_consumption"=hie_result))
  
  cat("Hybrid effect via food consumption (independently of availability):\n ")
  hybrid_indirect_effect2 <- apply(combined_boot_results %>% dplyr::select(orfcs_ad,hints_cd),1,prod)
  hie_result <- summarize_calculated_effect(hybrid_indirect_effect2)
  hybrid_effect_set <- append(hybrid_effect_set,list("consumption_alone"=hie_result))
  
  hybrid_effect_set_df <- do.call(rbind,hybrid_effect_set)
  hybrid_effect_set_df$outcome<-effect_name
  hybrid_effect_set_df$pathway <- rownames(hybrid_effect_set_df)
  
  hybrid_effect_list<-append(hybrid_effect_list,list(hybrid_effect_set_df))
  
  
  #"The total effect is the sum of the direct and indirect effects"
  # - https://www.annualreviews.org/doi/pdf/10.1146/annurev-publhealth-032315-021402
  #there are three total effects we want to calculate: ORFCS, HINTS, and hybrid
  #For these path models we need to sum up all paths (the different kinds of indirect effects)
  #so for ORFCS this is going to be:
  #orfcs_ab*orfcs_bc*orfcs_cd*orfcs_de
  #orfcs_ab*orfcs_bc*orfcs_ce
  #orfcs_ab*orfcs_bd*orfcs_de
  #orfcs_ab*orfcs_be
  #orfcs_ac*orfcs_cd*orfcs_de
  #orfcs_ac*orfcs_ce
  #orfcs_ad*orfcs_de
  #orfcs_ae
  calculate_path_effect<-function(path_vector){
    return(apply(combined_boot_results[,path_vector],1,prod))
  }
  cat("total effect of the ORFCS model:\n")
  total_effect_orfcs<-(
    calculate_path_effect(paste0("orfcs_",c("ab","bc","cd","de")))+
      calculate_path_effect(paste0("orfcs_",c("ab","bc","ce")))+
      calculate_path_effect(paste0("orfcs_",c("ab","bd","de")))+
      calculate_path_effect(paste0("orfcs_",c("ab","be")))+
      calculate_path_effect(paste0("orfcs_",c("ac","cd","de")))+
      calculate_path_effect(paste0("orfcs_",c("ac","ce")))+
      calculate_path_effect(paste0("orfcs_",c("ad","de")))+
      combined_boot_results$orfcs_ae
  )
  hie_result <- summarize_calculated_effect(total_effect_orfcs)
  hybrid_effect_set <- append(hybrid_effect_set,list("total_effect_orfcs"=hie_result))
  
  cat("total effect of the HINTS model:\n")
  total_effect_hints<-(
    calculate_path_effect(paste0("hints_",c("ab","bc","cd")))+
      calculate_path_effect(paste0("hints_",c("ab","bd")))+
      calculate_path_effect(paste0("hints_",c("ac","cd")))+
      combined_boot_results$hints_ad
  )
  hie_result <- summarize_calculated_effect(total_effect_hints)
  hybrid_effect_set <- append(hybrid_effect_set,list("total_effect_hints"=hie_result))
  
  cat("HINTS proportion mediated:\n")
  hints_prop_mediated<-HINTS_indirect_effect/total_effect_hints
  hie_result <- summarize_calculated_effect(hints_prop_mediated)
  hybrid_effect_set <- append(hybrid_effect_set,list("hints_prop_mediated"=hie_result))
  
  
  cat("total effect of the hybrid model:\n")
  total_effect_hybrid<-(
    calculate_path_effect(c(paste0("orfcs_",c("bc","cd")),paste0("hints_",c("ab","cd"))))+
      #calculate_path_effect(c(paste0("orfcs_",c("ab","bc","ce")),paste0("hints_",c("ab","bc","ce"))))+
      calculate_path_effect(paste0("hints_",c("ab","bc","cd")))+
      calculate_path_effect(c(paste0("hints_",c("ab","bd"))))+
      calculate_path_effect(c(paste0("orfcs_",c("ac","cd")),paste0("hints_",c("cd"))))+
      #calculate_path_effect(c(paste0("orfcs_",c("ac","ce")),paste0("hints_",c("ac","ce"))))+
      calculate_path_effect(c(paste0("hints_",c("ac","cd"))))+
      combined_boot_results$hints_ad
  )
  
  hie_result <- summarize_calculated_effect(total_effect_hybrid)
  hybrid_effect_set <- append(hybrid_effect_set,list("total_effect_hybrid"=hie_result))

  cat("hybrid proportion mediated:\n")
  hints_prop_mediated<-hybrid_main_indirect_effect/total_effect_hybrid
  hie_result <- summarize_calculated_effect(hints_prop_mediated)
  hybrid_effect_set <- append(hybrid_effect_set,list("hints_prop_mediated"=hie_result))
  

  cat("---------\n\n\n")

}

hybrid_effect_df<-do.call(rbind,hybrid_effect_list)

```

### Calculate total mediated and proportion mediated

```{r}
```

## With interaction terms



```{r}
get_fit_PE<-function(fit_to_read){
  sink("temp_out.txt")
  fit_pe<-summary(fit_to_read,ci=TRUE)$pe
  sink(NULL)
  return(fit_pe)
}

lavaan_results_list <- list()
for (hints_fit_label in names(hints_fits_by_outcome_int)){
  hints_fit<-hints_fits_by_outcome_int[[hints_fit_label]]
  lavaan_summarized_results <- get_fit_PE(hints_fit) %>% filter(label!="")
  lavaan_summarized_results[["outcome"]]<-hints_fit_label
  lavaan_results_list<-append(lavaan_results_list,list(lavaan_summarized_results))
}
lavaan_results_interaction_df <- do.call(rbind,lavaan_results_list)
```


```{r, warning=FALSE}



orfcs_boot<-extract_and_label_bootstrap_results(orfcs_fit_int)
colnames(orfcs_boot)<-
  paste0("orfcs_",colnames(orfcs_boot))

#raw_data_list<-list()

hybrid_effect_list <-list()
for (effect_name in names(hints_fits_by_outcome_int)){
  cat(paste0("HYBRID INDIRECT EFFECT FOR: ",effect_name,"\n\n"))
  hints_boot <-extract_and_label_bootstrap_results(hints_fits_by_outcome_int[[effect_name]])

    colnames(hints_boot)<-
    paste0("hints_",colnames(hints_boot))
  
  
  row_count <- min(nrow(orfcs_boot),nrow(hints_boot))
  combined_boot_results <- data.frame(cbind(orfcs_boot[1:row_count,],hints_boot[1:row_count,]))
  
  #raw_data_list[[effect_name]]<-combined_boot_results
  
  # cat("\n")

  cat("HINTS indirect effect (Control):\n ")  
  combined_boot_results <- combined_boot_results %>% mutate(hints_indirect_control = hints_ab*hints_bc*hints_cd)
  HINTS_indirect_effect <- combined_boot_results$hints_indirect_control
  summarize_calculated_effect(HINTS_indirect_effect)
  
  cat("HINTS indirect effect (Treatment):\n ")  
  combined_boot_results <- combined_boot_results %>% mutate(
    hints_bc_treat = hints_bc+hints_bc_g,
    hints_cd_treat = hints_cd+hints_cd_g,
    hints_indirect_treat = hints_ab*hints_bc_treat*hints_cd_treat,
    hints_indirect_treat_diff = hints_indirect_treat - hints_indirect_control
  )
  HINTS_indirect_effect <- combined_boot_results$hints_indirect_treat
  summarize_calculated_effect(HINTS_indirect_effect)
  
  cat("HINTS direct effect:\n ")  
  HINTS_direct_effect <- combined_boot_results$hints_ad
  hie_result<- summarize_calculated_effect(HINTS_direct_effect)
  hybrid_effect_set<-list("indirect_effect_cont"=hie_result)
  
  cat("Hybrid indirect effect (Control):\n ")
  combined_boot_results <- combined_boot_results %>% mutate(
    hybrid_main_indirect_cont = hints_ab*orfcs_bc*orfcs_cd*hints_cd
  )
  hie_result <- summarize_calculated_effect(combined_boot_results$hybrid_main_indirect_cont)
  hybrid_effect_set<-list("indirect_effect_cont"=hie_result)
  
  cat("Hybrid indirect effect (Treatment):\n ")
  combined_boot_results <- combined_boot_results %>% mutate(
    orfcs_bc_treat = orfcs_bc+orfcs_bc_g,
    orfcs_cd_treat = orfcs_cd+orfcs_cd_g,
    hybrid_main_indirect_treat = hints_ab*orfcs_bc_treat*orfcs_cd_treat*hints_cd_treat,
    hybrid_main_indirect_cont_treat_diff = hybrid_main_indirect_treat - hybrid_main_indirect_cont
  )
  hie_result <- summarize_calculated_effect(combined_boot_results$hybrid_main_indirect_treat)
  hybrid_effect_set<-list("indirect_effect_treat"=hie_result)
  
  cat("Hybrid indirect effect (Treatment-Control):\n ")
  hie_result <- summarize_calculated_effect(combined_boot_results$hybrid_main_indirect_cont_treat_diff)
  hybrid_effect_set<-list("hybrid_main_indirect_cont_treat_diff"=hie_result)
  
  
  
  cat("Hybrid effect via food availability and consumption:\n ")
  hybrid_indirect_effect1 <- apply(combined_boot_results %>% dplyr::select(orfcs_ac,orfcs_cd, hints_cd),1,prod)
  hie_result <- summarize_calculated_effect(hybrid_indirect_effect1)
  hybrid_effect_set <- append(hybrid_effect_set,list("availability_consumption"=hie_result))
  
  cat("Hybrid effect via food consumption (independently of availability):\n ")
  hybrid_indirect_effect2 <- apply(combined_boot_results %>% dplyr::select(orfcs_ad,hints_cd),1,prod)
  hie_result <- summarize_calculated_effect(hybrid_indirect_effect2)
  hybrid_effect_set <- append(hybrid_effect_set,list("consumption_alone"=hie_result))
  
  hybrid_effect_set_df <- do.call(rbind,hybrid_effect_set)
  hybrid_effect_set_df$outcome<-effect_name
  hybrid_effect_set_df$pathway <- rownames(hybrid_effect_set_df)
  
  hybrid_effect_list<-append(hybrid_effect_list,list(hybrid_effect_set_df))
  
  
  #"The total effect is the sum of the direct and indirect effects"
  # - https://www.annualreviews.org/doi/pdf/10.1146/annurev-publhealth-032315-021402
  #there are three total effects we want to calculate: ORFCS, HINTS, and hybrid
  #For these path models we need to sum up all paths (the different kinds of indirect effects)
  #so for ORFCS this is going to be:
  #orfcs_ab*orfcs_bc*orfcs_cd*orfcs_de
  #orfcs_ab*orfcs_bc*orfcs_ce
  #orfcs_ab*orfcs_bd*orfcs_de
  #orfcs_ab*orfcs_be
  #orfcs_ac*orfcs_cd*orfcs_de
  #orfcs_ac*orfcs_ce
  #orfcs_ad*orfcs_de
  #orfcs_ae
  calculate_path_effect<-function(path_vector){
    return(apply(combined_boot_results[,path_vector],1,prod))
  }
  cat("total effect of the ORFCS model:\n")
  total_effect_orfcs<-(
    calculate_path_effect(paste0("orfcs_",c("ab","bc","cd","de")))+
      calculate_path_effect(paste0("orfcs_",c("ab","bc","ce")))+
      calculate_path_effect(paste0("orfcs_",c("ab","bd","de")))+
      calculate_path_effect(paste0("orfcs_",c("ab","be")))+
      calculate_path_effect(paste0("orfcs_",c("ac","cd","de")))+
      calculate_path_effect(paste0("orfcs_",c("ac","ce")))+
      calculate_path_effect(paste0("orfcs_",c("ad","de")))+
      combined_boot_results$orfcs_ae
  )
  hie_result <- summarize_calculated_effect(total_effect_orfcs)
  hybrid_effect_set <- append(hybrid_effect_set,list("total_effect_orfcs"=hie_result))
  
  cat("total effect of the HINTS model:\n")
  total_effect_hints<-(
    calculate_path_effect(paste0("hints_",c("ab","bc","cd")))+
      calculate_path_effect(paste0("hints_",c("ab","bd")))+
      calculate_path_effect(paste0("hints_",c("ac","cd")))+
      combined_boot_results$hints_ad
  )
  hie_result <- summarize_calculated_effect(total_effect_hints)
  hybrid_effect_set <- append(hybrid_effect_set,list("total_effect_hints"=hie_result))
  
  cat("HINTS proportion mediated:\n")
  hints_prop_mediated<-HINTS_indirect_effect/total_effect_hints
  hie_result <- summarize_calculated_effect(hints_prop_mediated)
  hybrid_effect_set <- append(hybrid_effect_set,list("hints_prop_mediated"=hie_result))
  
  
  # cat("total effect of the hybrid model:\n")
  # total_effect_hybrid<-(
  #   calculate_path_effect(c(paste0("orfcs_",c("bc","cd")),paste0("hints_",c("ab","cd"))))+
  #     #calculate_path_effect(c(paste0("orfcs_",c("ab","bc","ce")),paste0("hints_",c("ab","bc","ce"))))+
  #     calculate_path_effect(paste0("hints_",c("ab","bc","cd")))+
  #     calculate_path_effect(c(paste0("hints_",c("ab","bd"))))+
  #     calculate_path_effect(c(paste0("orfcs_",c("ac","cd")),paste0("hints_",c("cd"))))+
  #     #calculate_path_effect(c(paste0("orfcs_",c("ac","ce")),paste0("hints_",c("ac","ce"))))+
  #     calculate_path_effect(c(paste0("hints_",c("ac","cd"))))+
  #     combined_boot_results$hints_ad
  # )
  # 
  # hie_result <- summarize_calculated_effect(total_effect_hybrid)
  # hybrid_effect_set <- append(hybrid_effect_set,list("total_effect_hybrid"=hie_result))
  # 
  # cat("hybrid proportion mediated:\n")
  # hints_prop_mediated<-hybrid_main_indirect_effect/total_effect_hybrid
  # hie_result <- summarize_calculated_effect(hints_prop_mediated)
  # hybrid_effect_set <- append(hybrid_effect_set,list("hints_prop_mediated"=hie_result))
  

  cat("---------\n\n\n")

}

interaction_hybrid_effect_df<-do.call(rbind,hybrid_effect_list)

```


## Notes

On its face, this "hybrid effect" shows that if we assume relationships between (a) household income and health food availability and (b) health food availability and fruit and veggie consumption are the same in the HINTS population as they are in the ORFCS population, then rurality has an indirect effect through health food availability in HINTS, too.

# Summarizing the HINTS dataset results

Because there are quite a lot of results here, we should probably summarize them in a table.

### load data from HDD

```{r}
rdata_backup_filename = paste0("sequential_boot_",boot_times,"_int2.Rdata") 
if (exists("lavaan_results_df")){
  print("backing up data to hard disk")
  save.image(file=rdata_backup_filename)
}else{
  print('loading data from hard disk')
 load(file=rdata_backup_filename) 

}

#
```

```{r}
p_value_asterisks<-function(pvalue){
  p_value_asterisks_by_scalar <- function(pvalue){
    if (pvalue<0.001){
    return("***")
  }else if (pvalue<0.01){
    return("**")
  }else if (pvalue<0.05){
    return("*")
  }else if (pvalue<0.1){
    return("+")
  }
  return("")
  }
  return(sapply(pvalue,p_value_asterisks_by_scalar))
}
library(papaja)
library(kableExtra)
```

```{r}
library(dplyr)
```

```{r}

p_value_asterisks<-function(pvalue){
  p_value_asterisks_by_scalar <- function(pvalue){
    if (pvalue<0.001){
    return("***")
  }else if (pvalue<0.01){
    return("**")
  }else if (pvalue<0.05){
    return("*")
  }else if (pvalue<0.1){
    return("âº")
  }
  return("")
  }
  return(sapply(pvalue,p_value_asterisks_by_scalar))
}


formatB<-function(num,digits=digits){
  #FormatBen
  #return(str_replace(format(round(num,digits=digits),justify="right",scientific=FALSE)," ","&nbsp;"))
  return(format(round(num,digits=digits),scientific=FALSE))
}

num_w_p <- function(num, pvalue,digits=2){
  
  return(paste0(formatB(num,digits=digits),p_value_asterisks(pvalue)))
}
#can use this function for all sorts of labels, not just a particular kind
label_rename<-function(label){
  #effect routes
  label[label=="effect_via_fruit_vege_only"]<-"Via fruit and vegetable consumption"
  label[label=="effect_via_inc_only"]<-"Via income only"
  label[label=="availability_consumption"]<-"Via fruit and vegetable availability and consumption"
  label[label=="consumption_alone"]<-"Via fruit and vegetable consumption alone"
  
  #Outcome labels
  label[label=="GeneralHealth_i"] <- "Self-rated health"
  label[label=="MedConditionsAggregate"] <- "Aggregate cardiometabolic health"
  label[label=="MedConditions_HighBP_i"] <- "High blood pressure/hypertension"
  label[label=="EverHadCancer_i"] <- "Ever had cancer"
  #BMI"                    "GeneralHealth_i"        "MedConditionsAggregate" "MedConditions_HighBP_i" "EverHadCancer_i"   
  
  
  #misc
  label <- sapply(
    label,
    function(l){
      if(l=="BMI") return(l)
      return(str_replace_all(l,"_"," ") %>% str_to_sentence)
    }
  )
    
  return(label)
}

format_CI <- function(ci_lower, ci_upper,digits=digits){
  ci_lower_str <- formatB(ci_lower,digits=digits)
  ci_upper_str <- formatB(ci_upper,digits=digits)
  return(paste0("[",ci_lower_str,", ",ci_upper_str,"]"))
}

```


```{r}

kable_input <- lavaan_results_df %>% filter(label %in% c(
  "indirect_effect",
  "effect_via_inc_only",
  "effect_via_fruit_vege_only",
  "direct_effect"
  )) %>%
  mutate(Pathway = label_rename(label),
         Outcome = label_rename(outcome),
         Estimate = num_w_p(est,pvalue,digits=4),
         CI = format_CI(ci.lower,ci.upper,digits=4)
         #SE=formatB(se,digits=4)
         ) %>%
  arrange(outcome) %>%
  dplyr::select(Pathway, Outcome,Estimate,CI) %>% arrange(Pathway)

groups_df <- kable_input %>%
  group_by(Pathway) %>% 
    summarize(group_start=length(Pathway))

groups<-groups_df$group_start
names(groups)<-groups_df$Pathway

kable_out <- kable_input %>% 
  dplyr::select(-Pathway) %>%
  knitr::kable() %>% 
  kable_classic(full_width = F,html_font="Times New Roman") %>%
  pack_rows(index=groups)
  

#knitr::asis_output(str_replace(kable_out,"\\+","\\^\\+"))

kable_out


```

# Summarizing the hybrid dataset results

```{r}


kable_input <- hybrid_effect_df %>%
  #mutate(pv = p_value_asterisks(pvalue)) %>%
  mutate(Pathway = label_rename(pathway),
         Outcome = label_rename(outcome),
         Estimate = num_w_p(est,pvalue,digits=4),
         CI = format_CI(ci_lower,ci_upper,digits=4)
         #SE=formatB(se,digits=4)
         ) %>%
  dplyr::select(Pathway, Outcome,Estimate,CI) %>% arrange(Pathway)

groups_df <- kable_input %>%
  group_by(Pathway) %>% 
    summarize(group_start=length(Outcome))

groups<-groups_df$group_start
names(groups)<-groups_df$Pathway

rownames(kable_input)<-NULL
kable_input %>% 
  dplyr::select(-Pathway) %>%
  knitr::kable() %>% 
  kable_classic(full_width = F,html_font="Times New Roman") %>%
  
  #pack_rows(index=c("indirect_effect"=nrow(kable_input)))
  pack_rows(index=groups)
  




```

# Investigating additional factors

## household income

We probably could get household income from ORFCS because we have ZIP codes. First we need to get some mean data...

```{r}
orfcs_dataset_pp$ZipcodeMedianHouseholdIncome_c <- 
  orfcs_dataset_pp$ZipcodeMedianHouseholdIncome - mean(orfcs_dataset_pp$ZipcodeMedianHouseholdIncome,na.rm=TRUE)

orfcs_dataset_pp$ZipcodeMedianHouseholdIncome_z <- 
  zscore(orfcs_dataset_pp$ZipcodeMedianHouseholdIncome)
```

now we have it...

```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


# mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
# mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

# [1] "RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported + RaceC2_WhiteOnly"
# [1] "Gender3C_Female + Gender3C_Male + Gender3C_Other"

#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
oregon_model_with_zipinc=
"
  #Regressions
  ZipcodeMedianHouseholdIncome_z ~ ab*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  MESA_healthyfoodavailability_z ~ bc*ZipcodeMedianHouseholdIncome_z + ac*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  FFQ_fruit_vegetables_z ~ cd*MESA_healthyfoodavailability_z + bd*ZipcodeMedianHouseholdIncome_z + ad*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  (OUTCOMEVAR) ~ de*FFQ_fruit_vegetables_z + ce*MESA_healthyfoodavailability_z + be*ZipcodeMedianHouseholdIncome_z + ae*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
  
  
  #Defined Parameters:
  indirect_effect := ab*bc*cd*de
  d_rural_food_availability := ac
  id_rural_food_availability := ab*bc
  effect_via_income := ab*be
  rural_inc_consump := ab*bd*de
  direct_effect := ae
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI"#,
  #"GeneralHealth_i",
  #"MedConditionsAggregate",
  #"MedConditions_HighBP_i",
  #"EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )


```

So we built a simple model that replaces household income with ZIPCode Household Income. What does that look like?

```{r}


# for (outcome_var in outcome_measures){
set.seed(8233042)
outcome_var <- "BMI"
oregon_model_w_outcome <- str_replace_all(oregon_model_with_zipinc,"\\(OUTCOMEVAR\\)",outcome_var)
cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
cat(oregon_model_w_outcome)
orfcs_fit=sem(
  oregon_model_w_outcome,
  orfcs_dataset_pp,
  se = "bootstrap",
  bootstrap=boot_times,
  likelihood = "wishart")

summary(orfcs_fit,ci=TRUE)
  # cat("-----\n\n\n")
# }
```

```{r mediation_aSES}
set.seed(2498714)

library(mediation)

data_to_measure <- orfcs_dataset %>% dplyr::filter(!is.na(BMI)) %>% dplyr::filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(aSES_02_z~RuralZIP_i+Gender3C+DEMO_Age_c+I(DEMO_Age_c^2)+RaceC2+PSS_z#+
         ,data_to_measure)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+I(DEMO_Age_c^2)+RaceC2+aSES_02_z+PSS_z#+
         ,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times,boot=TRUE,boot.ci.type = "bca",
                          treat="RuralZIP_i",mediator="aSES_02_z")
summary(mediate_result,ci=TRUE)
plot(mediate_result)

summary(mc,ci=TRUE)
```

```{r mediation2_MedianHouseholdIncome}
set.seed(2498714)

library(mediation)

data_to_measure <- orfcs_dataset %>% dplyr::filter(!is.na(BMI)) %>% dplyr::filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI

mb <- lm(ZipcodeMedianHouseholdIncome~RuralZIP_i+Gender3C+DEMO_Age_c+I(DEMO_Age_c^2)+RaceC2+PSS_z#+
         ,data_to_measure)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+I(DEMO_Age_c^2)+RaceC2+ZipcodeMedianHouseholdIncome+PSS_z#+
         ,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times,boot=TRUE,boot.ci.type = "bca",
                          treat="RuralZIP_i",mediator="ZipcodeMedianHouseholdIncome")
summary(mediate_result,ci=TRUE)
plot(mediate_result,ci=TRUE)

summary(mc,ci=TRUE)
```

With this analysis I would tend to think we don't need to proceed to use Zipcode Median Household Income. It would tend to make the analysis more complicated, but what are the benefits? Primarily, it seems to be more strongly related to rurality (z=-14 for Zipcode household median income, compared to z=-4 for household income). However, it is not more strongly related to healthy food availability and SES. Finally, it is *less* strongly related to BMI; household income predicts BMI (z=-3.4) but zipcode median income does not (z=0.9). Because BMI is a variable of interest, or at least a proxy thereof, that seems to be the determining factor. If we include Zipcode Median household income, that will complicate the model without obvious benefit.

## Hours worked

Neither study records hours worked, although both record work status (full time/part time/unemployed). These would probably be predictive, but are not of particular interest, and I'm not aware of how we'd interpret this any differently to income, which is already included in the model.

# Pruning/regularization Oregon dataset

We can cut the dataset down, and perhaps observe slightly larger effects, by cutting the dataset down to size. Suitable rules might be:

-   Include all possible pathways to start with

-   Of the beta estimates with p\>0.1 and which are not part of a p\>0.1 pathway, remove the least significant

-   Test for goodness of fit. If it's an improvement, keep variable out and repeat. If it's not an improvement, keep it in and repeat

-   Repeat until there are no variables to take out.

-   

    ```{r}
    oregon_full_model_template=
    "
      #Regressions
      aSES_02_z ~ ab*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      MESA_healthyfoodavailability_z ~ bc*aSES_02_z + ac*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      FFQ_fruit_vegetables_z ~ cd*MESA_healthyfoodavailability_z + bd*aSES_02_z + ad*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      (OUTCOMEVAR) ~ de*FFQ_fruit_vegetables_z + ce*MESA_healthyfoodavailability_z + be*aSES_02_z + ae*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      
      #Defined Parameters:
      indirect_effect := ab*bc*cd*de
      #cut one parameter
      effect_abce :=ab*bc*ce #makes no particular theoretical sense but for regularization rules, I want to observe it
      effect_via_food := ac*cd*de
      effect_via_inc_eating := ab*bd*de
      #cut two parameters
      effect_via_income := ab*be
      effect_ace := ac*ce
      effect_via_eating := ad*de
      #cut all mediators
      direct_effect := ae
    "

    # - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

    outcome_measures <- c(
      "BMI"#,
      #"GeneralHealth_i",
      #"MedConditionsAggregate",
      #"MedConditions_HighBP_i",
      #"EverHadCancer_i"#no cancer for now, doesn't seem very important.
      )



    ```

OK, so we have set a full model. Let's run the base full model in SEM and follow the steps above to do the first pruning iteration.

```{r}
library(performance)

# for (outcome_var in outcome_measures){
set.seed(8233042)
outcome_var <- "BMI"
oregon_model_w_outcome <- str_replace_all(oregon_full_model_template,"\\(OUTCOMEVAR\\)",outcome_var)
cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
cat(oregon_model_w_outcome)
orfcs_fit_full=sem(
  oregon_model_w_outcome,
  orfcs_dataset_pp,
  se = "bootstrap",
  bootstrap=boot_times,
  likelihood = "wishart")

summary(orfcs_fit_full,fit.measures=TRUE,ci=TRUE)
  # cat("-----\n\n\n")
# }



```

```{r}
model_performance(orfcs_fit_full,metrics = c("Chi2","AGFI","CFI","RMSEA","p_RMSEA","AIC","BIC","Loglikelihood"))
```

OK. So now, let's try removing something. Of the model variables, ce was the least significant. That's the path directly from availability to outcomes, excluding consumption. So we'll remove it, and try again.

## first pruning

    ```{r}
    oregon_model_template_prune1=
    "
      #Regressions
      aSES_02_z ~ ab*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      MESA_healthyfoodavailability_z ~ bc*aSES_02_z + ac*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      FFQ_fruit_vegetables_z ~ cd*MESA_healthyfoodavailability_z + bd*aSES_02_z + ad*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      (OUTCOMEVAR) ~ de*FFQ_fruit_vegetables_z #+ ce*MESA_healthyfoodavailability_z 
               + be*aSES_02_z + ae*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      
      #Defined Parameters:
      indirect_effect := ab*bc*cd*de
      #cut one parameter
      #effect_abce :=ab*bc*ce #makes no particular theoretical sense but for regularization rules, I want to observe it
      effect_via_food := ac*cd*de
      effect_via_inc_eating := ab*bd*de
      #cut two parameters
      effect_via_income := ab*be
      #effect_ace := ac*ce
      effect_via_eating := ad*de
      #cut all mediators
      direct_effect := ae
    "

    ```

```{r}

# for (outcome_var in outcome_measures){
set.seed(8233042)
outcome_var <- "BMI"
oregon_model_w_outcome <- str_replace_all(oregon_model_template_prune1,"\\(OUTCOMEVAR\\)",outcome_var)
cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
cat(oregon_model_w_outcome)
orfcs_fit_prune1=sem(
  oregon_model_w_outcome,
  orfcs_dataset_pp,
  se = "bootstrap",
  bootstrap=boot_times,
  likelihood = "wishart")

summary(orfcs_fit_prune1,ci=TRUE)
  # cat("-----\n\n\n")
# }

```

```{r}
compare_performance(orfcs_fit_full,orfcs_fit_prune1,metrics = c("Chi2","AGFI","CFI","RMSEA","p_RMSEA","AIC","BIC","Loglikelihood"))
```

OK, the model looks good, and on BIC, the pruned model is an improvement. so let's cut out another variable.

Examinig the data, the next one to cut is bd, linking income to eating behavior (bypassing food availability). This is in one pathway, "effect via income and eating", and that pathway is not significant (p\>0.1). So we remove it and try again.

## Second pruning

    ```{r}
    oregon_model_template_prune2=
    "
      #Regressions
      aSES_02_z ~ ab*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      MESA_healthyfoodavailability_z ~ bc*aSES_02_z + ac*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      FFQ_fruit_vegetables_z ~ cd*MESA_healthyfoodavailability_z + #bd*aSES_02_z + 
                            ad*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      (OUTCOMEVAR) ~ de*FFQ_fruit_vegetables_z #+ ce*MESA_healthyfoodavailability_z 
               + be*aSES_02_z + ae*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      
      #Defined Parameters:
      indirect_effect := ab*bc*cd*de
      #cut one parameter
      #effect_abce :=ab*bc*ce #makes no particular theoretical sense but for regularization rules, I want to observe it
      effect_via_food := ac*cd*de
      #effect_via_inc_eating := ab*bd*de
      #cut two parameters
      effect_via_income := ab*be
      #effect_ace := ac*ce
      effect_via_eating := ad*de
      #cut all mediators
      direct_effect := ae
    "

    ```

```{r}

# for (outcome_var in outcome_measures){
set.seed(8233042)
outcome_var <- "BMI"
oregon_model_w_outcome <- str_replace_all(oregon_model_template_prune2,"\\(OUTCOMEVAR\\)",outcome_var)
cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
cat(oregon_model_w_outcome)
orfcs_fit_prune2=sem(
  oregon_model_w_outcome,
  orfcs_dataset_pp,
  se = "bootstrap",
  bootstrap=boot_times,
  likelihood = "wishart")

summary(orfcs_fit_prune2,ci=TRUE)
  # cat("-----\n\n\n")
# }

```

```{r}
compare_performance(orfcs_fit_full,orfcs_fit_prune1,orfcs_fit_prune2,metrics = c("Chi2","AGFI","CFI","RMSEA","p_RMSEA","AIC","BIC","Loglikelihood"))
```

The next pruning again looks like an improvement on BIC and mabye on AIC. So we can proceed to a third pruning. Direct effect of rurality on eating, `ad`, isn't significant, and neither is the path that uses it. So we can eliminate it and try again.

## Third pruning

    ```{r}
    oregon_model_template_prune3=
    "
      #Regressions
      aSES_02_z ~ ab*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      MESA_healthyfoodavailability_z ~ bc*aSES_02_z + ac*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      FFQ_fruit_vegetables_z ~ cd*MESA_healthyfoodavailability_z + #bd*aSES_02_z + ad*RuralZIP_i + 
                          DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      (OUTCOMEVAR) ~ de*FFQ_fruit_vegetables_z #+ ce*MESA_healthyfoodavailability_z 
               + be*aSES_02_z + ae*RuralZIP_i + DEMO_Age_c + DEMO_Age_c_pow2 + Gender3C_Male + Gender3C_Other + RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported
      
      
      #Defined Parameters:
      indirect_effect := ab*bc*cd*de
      #cut one parameter
      #effect_abce :=ab*bc*ce #makes no particular theoretical sense but for regularization rules, I want to observe it
      effect_via_food := ac*cd*de
      #effect_via_inc_eating := ab*bd*de
      #cut two parameters
      effect_via_income := ab*be
      #effect_ace := ac*ce
      #effect_via_eating := ad*de
      #cut all mediators
      direct_effect := ae
    "

    ```

```{r}

# for (outcome_var in outcome_measures){
set.seed(8233042)
outcome_var <- "BMI"
cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
cat(oregon_model_w_outcome)
oregon_model_w_outcome <- str_replace_all(oregon_model_template_prune3,"\\(OUTCOMEVAR\\)",outcome_var)
orfcs_fit_prune3=sem(
  oregon_model_w_outcome,
  orfcs_dataset_pp,
  se = "bootstrap",
  bootstrap=boot_times,
  likelihood = "wishart")

summary(orfcs_fit_prune3,fit.measures=TRUE,ci=TRUE)
  # cat("-----\n\n\n")
# }

```

```{r}
compare_performance(
  orfcs_fit_full,
  orfcs_fit_prune1,
  orfcs_fit_prune2,
  orfcs_fit_prune3,
  metrics = c("Chi2","AGFI","CFI","RMSEA","p_RMSEA","AIC","BIC","Loglikelihood"))
```

At least according to BIC, this model is a better fit. All remaining path variables are significant, and remaining paths are either significant or marginally significant, so that's as far as it goes.

Knowing all of this, perhaps it's not a big deal for the HINTS dataset that it doesn't have separate variables for consumption and availability. they seem quite related.

All modeled variables are now significant at least at the p\>0.1 level, and in fact, they're all significant at the p\<0.01 level, so we are done pruning.
