---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

To run this script: 1. Download HINTS 5 datasets from <https://hints.cancer.gov/view-questions-topics/all-hints-questions.aspx> to your data folder. Download all cycles of the data. 2. In the data folder, unzip each dataset. 3. Change the location parameter for the `get_hints5` call in the block below to point to your data folder. 4. Run this script.

```{r message=FALSE, warning=FALSE}
Sys.setenv(R_CONFIG_ACTIVE = Sys.info()["nodename"])

library(dplyr)
library(lavaan)
source("HINTS_preprocessing.R")
source("orfcs_utilities.R")
hints5 <-get_hints5(location=config::get("hints_protected_data_folderpath"))
boot_times<-10000

zscore <- function(x){
    return((x-mean(x,na.rm=TRUE))/sd(x,na.rm=TRUE))
}
```

```{r}
# table(orfcs_dataset$RuralZIP_i,
#       orfcs_dataset$Gender3C,
#       orfcs_dataset$RaceCategorical=="HispanicAnyRace"
#       )
```

```{r}
sapply(c("Metropolitan", "Micropolitan", "Small town", "Rural"),
       function(cat){sum(grepl(cat,hints5$PR_RUCA_2010))}
       )
```

what's the variability between men and women

including exercise or energy expenditure

exercise can improve objective health without/before it changes BMI.

weight physical activity and food intake

low income women, particularly low income women head of households, are of particular concern, and possibly hispanic women

```{r}
#table(orfcs_dataset$RuralZIP_i,
#      orfcs_dataset$Gender3C,
#      orfcs_dataset$RaceCategorical=="HispanicAnyRace"
#      )
```


```{r}
table(hints5$GeneralHealth_of) %>% cumsum / sum(!is.na(hints5$GeneralHealth_of))

hist(as.integer(hints5$GeneralHealth_of))
```

```{r}
library(magrittr)
library(dplyr)



data_dir <- config::get("rural_data_dir")

preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed2_anon_by_subj.csv")
library(readr)
library(ggplot2)
library(GGally)
orfcs_dataset <- readr::read_csv(preprocessed_data_filepath)



```

Let's do our best to include all the same covariates we previously included.

# Prep

```{r}
library(stringi)
# [1] "Fruit_vegetables_z~HINTSIsRural_i+Age_c+I(Age_c^2)+RacePP+Gender3C+filename"
# [1] "MedConditions_HighBP_i~Fruit_vegetables_z+HINTSIsRural_i+Age_c+I(Age_c^2)+RacePP+Gender3C+filename"
# IncomeRanges_r

#need to do prepare variables so lavaan can process them
hints5_pp <- hints5
#add quadratic
hints5_pp$Age_c_pow2 <- hints5_pp$Age_c^2


#one-hot some variables
factor_to_clean_string <- function(data, col_to_stringify){
  data[[col_to_stringify]] <- as.character(data[[col_to_stringify]])
  data[[col_to_stringify]] <- (
    str_replace_all(data[[col_to_stringify]],"\\s","_") %>% 
      str_replace_all("\\W","")
  )#table(hints5_pp[[col_to_stringify]])
  return(data)
}

hints5_pp<-factor_to_clean_string(hints5_pp,"RacePP2")
hints5_pp$RacePP2<-factor(hints5_pp$RacePP2)
hints5_pp <- mltools::one_hot(hints5_pp,"RacePP2",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("RacePP2_",colnames(hints5_pp))],collapse=" + "))

hints5_pp<-factor_to_clean_string(hints5_pp,"Hisp_Cat2")
hints5_pp$Hisp_Cat2<-factor(hints5_pp$Hisp_Cat2,levels=names(sort(table(hints5_pp$Hisp_Cat2),decreasing = TRUE)))
hints5_pp <- mltools::one_hot(hints5_pp,"Hisp_Cat2",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("Hisp_Cat2_",colnames(hints5_pp))],collapse=" + "))

hints5_pp<-factor_to_clean_string(hints5_pp,"Gender3C")
hints5_pp$Gender3C<-factor(hints5_pp$Gender3C)
hints5_pp <- mltools::one_hot(hints5_pp,"Gender3C",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("Gender3C_",colnames(hints5_pp))],collapse=" + "))



```

Now prepare the ORFCS dataset for lavaan.

```{r}
#need to do prepare variables so lavaan can process them
orfcs_dataset_pp <- data.table(orfcs_dataset)
#add quadratic
orfcs_dataset_pp$DEMO_Age_c_pow2 <- orfcs_dataset_pp$DEMO_Age_c^2


#one-hot some variables


orfcs_dataset_pp<-factor_to_clean_string(orfcs_dataset_pp,"RaceC2")
orfcs_dataset_pp$RaceC2<-factor(orfcs_dataset_pp$RaceC2)
orfcs_dataset_pp <- mltools::one_hot(orfcs_dataset_pp,"RaceC2",dropCols = FALSE)
print(paste0(colnames(orfcs_dataset_pp)[grepl("RaceC2_",colnames(orfcs_dataset_pp))],collapse=" + "))

orfcs_dataset_pp<-factor_to_clean_string(orfcs_dataset_pp,"Gender3C")
orfcs_dataset_pp$Gender3C<-factor(orfcs_dataset_pp$Gender3C)
orfcs_dataset_pp <- mltools::one_hot(orfcs_dataset_pp,"Gender3C",dropCols = FALSE)
print(paste0(colnames(orfcs_dataset_pp)[grepl("Gender3C_",colnames(orfcs_dataset_pp))],collapse=" + "))
```

# Descriptive statistics

```{r}

cor.test(orfcs_dataset_pp$FFQ_fruit_vegetables_z,orfcs_dataset_pp$cancer_promoting_minus_preventing_FFQ_z)
```

# Oregon dataset: basic disparity

# HINTS dataset: two mediators

This follows Hayes PROCESS Model 6 with two mediators but we are doing it here in Lavaan.

Variables are:

-   Treatment: Rurality
-   Two Mediators: household income, and fruit and vegetable consumption, in that order.
-   Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure. (and cancer??)

This model below is adapted from <https://towardsdatascience.com/doing-and-reporting-a-serial-mediation-model-with-two-mediators-in-r-with-lavaan-739ed3155814>

I think they've left some things out. I need to do a bit more research to work out how to properly implement this, probably including a basic crash course in SEM.

For the basic HINTs lms, see `HINTS_health_outcomes.Rmd`.

```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
hints_model_template=
"
  #Regressions
  IncomeRanges_r ~ ab*HINTSIsRural_i
  
  Fruit_vegetables_z ~ bc*IncomeRanges_r + ac*HINTSIsRural_i
  
  (OUTCOMEVAR) ~ cd*Fruit_vegetables_z + bd*IncomeRanges_r + ad*HINTSIsRural_i
  
  
  #Defined Parameters:
  indirect_effect := ab*bc*cd
  effect_via_inc_only :=ab*bd
  effect_via_fruit_vege_only :=ac*cd
  direct_effect := ad
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI",
  "GeneralHealth_i",
  "MedConditionsAggregate",
  "MedConditions_HighBP_i",
  "EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```

```{r}



hints_fits_by_outcome<- list()

for (outcome_var in outcome_measures){
  set.seed(05711846)
  hints_model_w_outcome <- str_replace_all(hints_model_template,"\\(OUTCOMEVAR\\)",outcome_var)
  cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
  cat(hints_model_w_outcome)
  fit=sem(
    hints_model_w_outcome,
    hints5_pp,
    se = "bootstrap",
    bootstrap=boot_times,
    likelihood = "wishart")
  
  hints_fits_by_outcome[[outcome_var]]<-fit
  summary(fit,ci=TRUE)
  cat("-----\n\n\n")
}
```

```{r}
# 
# set.seed(05711846)
# 
# fit=sem(
#   hints_model,
#   hints5_pp,
#   se = "bootstrap",
#   bootstrap=1000,
#   likelihood = "wishart")
# summary(fit)
```

# Oregon dataset: three mediators

For comparison with HINTS, we'll first repeat the HINTS dataset two-mediator model as described above, but using three mediators.

Then, we'll proceed with our main Oregon dataset analysis.

This follows Hayes PROCESS Model 6 with THREE mediators but we are doing it here in Lavaan.

Variables are:

-   Treatment: Rurality
-   Two Mediators: household income, MESA healthy food availability, and fruit and vegetable consumption, in that order.
-   Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


# mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
# mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

# [1] "RaceC2_Asian + RaceC2_HawaiianOtherPacificIslander + RaceC2_HispanicAnyRace + RaceC2_OtherRaceRaceNotReported + RaceC2_WhiteOnly"
# [1] "Gender3C_Female + Gender3C_Male + Gender3C_Other"

#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
oregon_model_template=
"
  #Regressions
  aSES_02_z ~ ab*RuralZIP_i
  
  MESA_healthyfoodavailability_z ~ bc*aSES_02_z + ac*RuralZIP_i 
  
  FFQ_fruit_vegetables_z ~ cd*MESA_healthyfoodavailability_z + bd*aSES_02_z + ad*RuralZIP_i
  
  (OUTCOMEVAR) ~ de*FFQ_fruit_vegetables_z + ce*MESA_healthyfoodavailability_z + be*aSES_02_z + ae*RuralZIP_i
  
  
  #Defined Parameters:
  indirect_effect := ab*bc*cd*de
  effect_via_food := ac*cd*de
  effect_via_income := ab*be
  effect_via_inc_eating := ab*bd*de
  effect_via_eating := ad*de
  direct_effect := ae
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI"#,
  #"GeneralHealth_i",
  #"MedConditionsAggregate",
  #"MedConditions_HighBP_i",
  #"EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```

```{r}




# for (outcome_var in outcome_measures){
set.seed(8233042)
outcome_var <- "BMI"
oregon_model_w_outcome <- str_replace_all(oregon_model_template,"\\(OUTCOMEVAR\\)",outcome_var)
cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
cat(oregon_model_w_outcome)
orfcs_fit=sem(
  oregon_model_w_outcome,
  orfcs_dataset_pp,
  se = "bootstrap",
  bootstrap=boot_times,
  likelihood = "wishart")

summary(orfcs_fit,ci=TRUE)
  # cat("-----\n\n\n")
# }


```

# Hybrid: three mediators

This follows Hayes PROCESS Model 6 with THREE mediators. We need to somehow manually combine the two datasets by multiplying effects. Need to follow bootstrap analysis, which means we need to extract raw bootstrap results and combine them. I'm not sure it's feasible, but it would be quite valuable to do.

Variables are:

-   Treatment: Rurality
-   Two Mediators: household income, MESA healthy food availability, and fruit and vegetable consumption, in that order.
-   Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

## Hybrid Analysis run

```{r}
get_fit_PE<-function(fit_to_read){
  sink("temp_out.txt")
  fit_pe<-summary(fit_to_read,ci=TRUE)$pe
  sink(NULL)
  return(fit_pe)
}

lavaan_results_list <- list()
for (hints_fit_label in names(hints_fits_by_outcome)){
  hints_fit<-hints_fits_by_outcome[[hints_fit_label]]
  lavaan_summarized_results <- get_fit_PE(hints_fit) %>% filter(label!="")
  lavaan_summarized_results[["outcome"]]<-hints_fit_label
  lavaan_results_list<-append(lavaan_results_list,list(lavaan_summarized_results))
}
lavaan_results_df <- do.call(rbind,lavaan_results_list)
```

```{r, warning=FALSE}
source("gen_utilities.R")


orfcs_boot<-extract_and_label_bootstrap_results(orfcs_fit)
colnames(orfcs_boot)<-
  paste0("orfcs_",colnames(orfcs_boot))

hybrid_effect_list <-list()
for (effect_name in names(hints_fits_by_outcome)){
  cat(paste0("HYBRID INDIRECT EFFECT FOR: ",effect_name,"\n\n"))
  hints_boot <-extract_and_label_bootstrap_results(hints_fits_by_outcome[[effect_name]])
  # sink("temp_diversion.txt")
  # lavaan_computed_indirect_effect <- (
  #   summary(hints_fits_by_outcome[[effect_name]])$PE %>% filter(label=="indirect_effect")
  # )
  # sink(NULL)
  colnames(hints_boot)<-
    paste0("hints_",colnames(hints_boot))
  
  
  row_count <- min(nrow(orfcs_boot),nrow(hints_boot))
  combined_boot_results <- data.frame(cbind(orfcs_boot[1:row_count,],hints_boot[1:row_count,]))
  

  
  # cat("HINTS lavaan pre-computed indirect effect:\n")
  # cat(paste(names(lavaan_computed_indirect_effect),collapse="\t"))
  # cat(paste(lavaan_computed_indirect_effect,collapse="\t"))
  # 
  # cat("\n")

  cat("HINTS indirect effect:\n ")  
  HINTS_indirect_effect <- apply(combined_boot_results %>% select(hints_ab, hints_bc, hints_cd),1,prod)
  summarize_calculated_effect(HINTS_indirect_effect)
  
  
  cat("Hybrid indirect effect:\n ")
  hybrid_indirect_effect <- apply(combined_boot_results %>% select(hints_ab, orfcs_bc,orfcs_cd, hints_cd),1,prod)
  hie_result <- summarize_calculated_effect(hybrid_indirect_effect)
  hybrid_effect_set<-list("indirect_effect"=hie_result)
  
  cat("Hybrid effect via food availability and consumption:\n ")
  hybrid_indirect_effect <- apply(combined_boot_results %>% select(orfcs_ac,orfcs_cd, hints_cd),1,prod)
  hie_result <- summarize_calculated_effect(hybrid_indirect_effect)
  hybrid_effect_set <- append(hybrid_effect_set,list("availability_consumption"=hie_result))
  
  cat("Hybrid effect via food consumption (independently of availability):\n ")
  hybrid_indirect_effect <- apply(combined_boot_results %>% select(orfcs_ad,hints_cd),1,prod)
  hie_result <- summarize_calculated_effect(hybrid_indirect_effect)
  hybrid_effect_set <- append(hybrid_effect_set,list("consumption_alone"=hie_result))
  
  hybrid_effect_set_df <- do.call(rbind,hybrid_effect_set)
  hybrid_effect_set_df$outcome<-effect_name
  hybrid_effect_set_df$pathway <- rownames(hybrid_effect_set_df)
  
  hybrid_effect_list<-append(hybrid_effect_list,list(hybrid_effect_set_df))
  cat("---------\n\n\n")

}

hybrid_effect_df<-do.call(rbind,hybrid_effect_list)

```

## Notes

On its face, this "hybrid effect" shows that if we assume relationships between (a) household income and health food availability and (b) health food availability and fruit and veggie consumption are the same in the HINTS population as they are in the ORFCS population, then rurality has an indirect effect through health food availability in HINTS, too.

# Summarizing the HINTS dataset results

Because there are quite a lot of results here, we should probably summarize them in a table.

```{r}
#save.image(file=paste0("sequential_boot_no_confounders_",boot_times,".Rdata"))
#load(file=paste0("sequential_boot_no_confounders_",boot_times,".Rdata"))
```

```{r}
p_value_asterisks<-function(pvalue){
  p_value_asterisks_by_scalar <- function(pvalue){
    if (pvalue<0.001){
    return("***")
  }else if (pvalue<0.01){
    return("**")
  }else if (pvalue<0.05){
    return("*")
  }else if (pvalue<0.1){
    return("+")
  }
  return("")
  }
  return(sapply(pvalue,p_value_asterisks_by_scalar))
}
library(papaja)
library(kableExtra)
```

```{r}
library(dplyr)
```

```{r}

p_value_asterisks<-function(pvalue){
  p_value_asterisks_by_scalar <- function(pvalue){
    if (pvalue<0.001){
    return("***")
  }else if (pvalue<0.01){
    return("**")
  }else if (pvalue<0.05){
    return("*")
  }else if (pvalue<0.1){
    return("âº")
  }
  return("")
  }
  return(sapply(pvalue,p_value_asterisks_by_scalar))
}


formatB<-function(num,digits=digits){
  #FormatBen
  #return(str_replace(format(round(num,digits=digits),justify="right",scientific=FALSE)," ","&nbsp;"))
  return(format(round(num,digits=digits),scientific=FALSE))
}

num_w_p <- function(num, pvalue,digits=2){
  
  return(paste0(formatB(num,digits=digits),p_value_asterisks(pvalue)))
}
#can use this function for all sorts of labels, not just a particular kind
label_rename<-function(label){
  #effect routes
  label[label=="effect_via_fruit_vege_only"]<-"Via fruit and vegetable consumption"
  label[label=="effect_via_inc_only"]<-"Via income only"
  label[label=="availability_consumption"]<-"Via fruit and vegetable availability and consumption"
  label[label=="consumption_alone"]<-"Via fruit and vegetable consumption alone"
  
  #Outcome labels
  label[label=="GeneralHealth_i"] <- "Self-rated health"
  label[label=="MedConditionsAggregate"] <- "Aggregate cardiometabolic health"
  label[label=="MedConditions_HighBP_i"] <- "High blood pressure/hypertension"
  label[label=="EverHadCancer_i"] <- "Ever had cancer"
  #BMI"                    "GeneralHealth_i"        "MedConditionsAggregate" "MedConditions_HighBP_i" "EverHadCancer_i"   
  
  
  #misc
  label <- sapply(
    label,
    function(l){
      if(l=="BMI") return(l)
      return(str_replace_all(l,"_"," ") %>% str_to_sentence)
    }
  )
    
  return(label)
}



```


```{r}

kable_input <- lavaan_results_df %>% filter(label %in% c(
    "indirect_effect",
  "direct_effect",
  "effect_via_inc_only",
  "effect_via_fruit_vege_only")) %>%
  mutate(Pathway = label_rename(label),
         Outcome = label_rename(outcome),
         Estimate = num_w_p(est,pvalue,digits=4),
         SE=formatB(se,digits=4)) %>%
  arrange(outcome) %>%
  select(Pathway, Outcome,Estimate,SE) %>% arrange(Pathway)

groups_df <- kable_input %>%
  group_by(Pathway) %>% 
    summarize(group_start=length(Pathway))

groups<-groups_df$group_start
names(groups)<-groups_df$Pathway

kable_out <- kable_input %>% 
  select(-Pathway) %>%
  knitr::kable() %>% 
  kable_classic(full_width = F,html_font="Times New Roman") %>%
  pack_rows(index=groups)
  

#knitr::asis_output(str_replace(kable_out,"\\+","\\^\\+"))

kable_out


```

# Summarizing the hybrid dataset results

```{r}


kable_input <- hybrid_effect_df %>%
  #mutate(pv = p_value_asterisks(pvalue)) %>%
  mutate(Pathway = label_rename(pathway),
         Outcome = label_rename(outcome),
         Estimate = num_w_p(est,pvalue,digits=4),
         SE=formatB(se,digits=4)) %>%
  select(Pathway, Outcome,Estimate,SE) %>% arrange(Pathway)

groups_df <- kable_input %>%
  group_by(Pathway) %>% 
    summarize(group_start=length(Outcome))

groups<-groups_df$group_start
names(groups)<-groups_df$Pathway

rownames(kable_input)<-NULL
kable_input %>% 
  select(-Pathway) %>%
  knitr::kable() %>% 
  kable_classic(full_width = F,html_font="Times New Roman") %>%
  
  #pack_rows(index=c("indirect_effect"=nrow(kable_input)))
  pack_rows(index=groups)
  




```

