---
title: "Healthy environments are associated with lower BMIs controlling for race, gender, and age"
output:
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 4
---

This notebook tracks the healthy environment paper where we present a pre-registered finding that having a healthier food environment is associated with lower BMIs, controlling for race, gender, and age.

We'll work across two datasets here: DEV and ORFCS.

First, we need to do the pre-registered finding exactly as presented. It was for the ORFCS, so we need to load that first.

```{r}
Sys.setenv(R_CONFIG_ACTIVE = Sys.info()["nodename"])
library(stringr)
library(rstatix)
```

```{r}
library(magrittr)
library(dplyr)



data_dir <- config::get("rural_data_dir")

preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed2_anon_by_subj.csv")
#preprocessed_data_filepath <- paste0(config::get("orfcs_shareable_folder"),"oregon_dataset_anon.csv")
library(readr)
library(ggplot2)
library(GGally)
source("HINTS_preprocessing.R")
source("orfcs_utilities.R")
source("gen_utilities.R")

preprocessed_data <- readr::read_csv(preprocessed_data_filepath)
preprocessed_data <- generate_education_categorical(preprocessed_data)

orfcs_dataset<-preprocessed_data


```

```{r}
#put self-report items in z-score. It wont' change the estimate but it will make it easier to interpret
zscore <- function(x){
  return((x-mean(x,na.rm=TRUE))/sd(x,na.rm=TRUE))
}
orfcs_dataset %<>% 
  mutate(
    MESA_healthyfoodavailability_z =zscore(MESA_healthyfoodavailability),
    MESA_safetyfromcrime_z =zscore(MESA_safetyfromcrime),
    PSS_z = zscore(PSS_sum),
    cancer_promoting_minus_preventing_FFQ_z = zscore(cancer_promoting_minus_preventing_FFQ),
    DEMO_Age_c = DEMO_Age - mean(DEMO_Age,na.rm=TRUE), #center age, but do not z-score it.
    RaceC2 = factor(RaceC2,levels=names(sort(-table(orfcs_dataset$RaceC2))))
  )
```

```{r}
#https://www.rdocumentation.org/packages/mediation/versions/4.5.0/topics/mediate
library(mediation)
boot_times = 10000 # set this to 10000 for final analysis, and 100 for setting up
```

#Study 1


## summary stats and counts

```{r}
print(nrow(orfcs_dataset))
bmi_regression_dataset <- orfcs_dataset %>% filter(!is.na(BMI) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2))
                                                   
print(nrow(bmi_regression_dataset))
study_1_dataset<-orfcs_dataset %>% filter(!is.na(BMI) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2) & (Gender3C %in% c("Male", "Female")))
print(nrow(study_1_dataset))

```

## Rurality and physical health outcomes

### Regressions of Rurality on FFQ and BMI

```{r}

#orfcs_dataset %>% filter(is.na(BMI)) %>% dplyr::select(WEIGHT,HEIGHT_m) %>% is.na %>% colSums
orfcs_dataset %>% filter(!is.na(BMI) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2)) %>% .$RuralZIP %>% table
orfcs_dataset %>% filter(!is.na(cancer_promoting_minus_preventing_FFQ) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2)) %>% .$RuralZIP %>% table
predict_ffq_rural <- lm(cancer_promoting_minus_preventing_FFQ~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime+
                      PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
print(summary(predict_ffq_rural))
print(nrow(predict_ffq_rural$model))
print(confint(predict_ffq_rural))

predict_bmi_rural <- lm(BMI~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime
                      PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
print(summary(predict_bmi_rural))
print(nrow(predict_bmi_rural$model))
print(confint(predict_bmi_rural))

```




```{r}
apaTables::apa.reg.table(predict_ffq_rural,filename = "study_1_2_results_predict_ffq_from_rurality.doc")
```



```{r}
apaTables::apa.reg.table(predict_bmi_rural,filename = "study_1_2_results_predict_bmi_from_rurality.doc")
```

## Mediators of the relation of rurality to health outcomes


### Regression of HF Availability & Safety From Crime

```{r}


predict_bmi <- lm(BMI~
                    MESA_healthyfoodavailability_z+MESA_safetyfromcrime_z+PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_bmi)
confint(predict_bmi)

predict_ffq <- lm(cancer_promoting_minus_preventing_FFQ_z~
                    MESA_healthyfoodavailability_z+MESA_safetyfromcrime_z+PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_ffq)
confint(predict_ffq)
```


```{r}
library(papaja)
library(apaTables)
```

In each of these analyses, MESA_healthyfoodavailability is important, and is related to lower BMIs (b=-0.7, p<0.05) and FFQ (b=-0.07, p<0.001). That is, for every 1 SD in healthy food availability, we get -0.7 points on the BMI scale and -0.13 points on the z-scored Food Frequency Questionnaire.

### Repeat those regression with Age as a Quadratic

We can also measures these while controlling for age as a quadratic variable:


```{r}


predict_bmi <- lm(BMI~
                    MESA_healthyfoodavailability_z+MESA_safetyfromcrime_z+PSS_z+
                    DEMO_Age_c+I(DEMO_Age_c^2)+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_bmi)
confint(predict_bmi)

predict_ffq <- lm(cancer_promoting_minus_preventing_FFQ_z~
                    MESA_healthyfoodavailability_z+MESA_safetyfromcrime_z+PSS_z+
                    DEMO_Age_c+I(DEMO_Age_c^2)+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_ffq)
confint(predict_ffq)
```



```{r}
apaTables::apa.reg.table(predict_bmi,filename = "study_1_2_results_predict_bmi_from_food_availability.doc")
```




```{r}
apaTables::apa.reg.table(predict_ffq,filename = "study_1_2_results_predict_ffq_from_food_availability.doc")
```

## Key Mediation




```{r mediation1_zip_food_availability}
set.seed(6472426)
library(mediation)

orfcs_2g <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,orfcs_2g)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,orfcs_2g)

mediate_result <- mediate(mb,mc,sims=boot_times, boot=TRUE,boot.ci.type = "bca", treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
summary(mc)
confint(mc)
```



### Include an interaction term
```{r}
set.seed(6472426)
mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,orfcs_2g)
mc <- lm(BMI~RuralZIP_i*MESA_healthyfoodavailability_z+Gender3C+DEMO_Age_c+RaceC2+PSS_z,orfcs_2g)

mediate_result <- mediate(mb,mc,sims=boot_times, treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z",
                          boot=TRUE,boot.ci.type = "bca")
summary(mediate_result)
summary(mb)
confint(mb)
summary(mc)
confint(mc)

```

### Try adding IPAQ

```{r}

set.seed(6472426)
mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z + IPAQ_MET_kCal,orfcs_2g)
mc <- lm(BMI~RuralZIP_i+MESA_healthyfoodavailability_z+Gender3C+DEMO_Age_c+RaceC2+PSS_z+IPAQ_MET_kCal,orfcs_2g)

mediate_result <- mediate(mb,mc,sims=boot_times, treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z",
                          boot=TRUE,boot.ci.type = "bca")
summary(mediate_result)
summary(mb)
confint(mb)
summary(mc)
confint(mc)

```


```{r}

set.seed(6472426)
mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z + IPAQ_MET_kCal,orfcs_2g)
mc <- lm(BMI~RuralZIP_i+MESA_healthyfoodavailability_z+Gender3C+DEMO_Age_c+RaceC2+PSS_z,orfcs_2g)

mediate_result <- mediate(mb,mc,sims=boot_times, treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z",
                          boot=TRUE,boot.ci.type = "bca")
summary(mediate_result)
summary(mb)
confint(mb)
summary(mc)
confint(mc)
```


### Post-hoc with income, zip code income, and education as confounders

```{r}
unique(orfcs_2g$Education_Categorical)

```


```{r mediation1_zip_food_availability2}
set.seed(6472426)
library(mediation)

orfcs_2g$Education_Ordinal <- as.integer(orfcs_2g$Education_Categorical)
orfcs_2g$ZipcodeMedianHouseholdIncome_z <- zscore(orfcs_2g$ZipcodeMedianHouseholdIncome)

orfcs_2g$RaceC2<-factor(orfcs_2g$RaceC2,levels=names(sort(-table(orfcs_2g$RaceC2))))
#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z + aSES_02_z + ZipcodeMedianHouseholdIncome_z,orfcs_2g)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z + aSES_02_z + ZipcodeMedianHouseholdIncome,orfcs_2g)

mediate_result <- mediate(mb,mc,sims=boot_times, boot=TRUE,boot.ci.type = "bca", treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
summary(mb)
confint(mb)
summary(mc)
confint(mc)

```

